### 2022-05-18 Paper_draft.tex
Initial commit

\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{xcolor}
\newcommand\note[1]{\textcolor{red}{#1}}
\usepackage{amsmath}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

\begin{document}

\preprint{APS/123-QED}

\title{Methods for constructing the transition graphs of an interacting hysteron model}
\author{Margot Teunisse}
\author{Martin van Hecke}%
\affiliation{%
Universiteit Leiden
}%

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
\begin{description}
\item[Structure]
\end{description}
\end{abstract}

%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle

%\tableofcontents
\section{Introduction}
Frustrated media can have rugged energy landscapes, with many metastable states. Recent work has shown that the many metastable states in frustrated systems can lead to unusual pathways when the system is subject to driving. For a variety of systems, including sheared amorphous solids (Nagel, 2021; Keim \& Paulsen, 2019), crumpled thin sheets (Lahini, 2021), corrugated sheets (Bense, 2021) and origami structures (Lechenault, 2021) remarkable phenomena such as breaking of return-point memory, a multiperiodic response to cyclical driving, and transient memory as described by the park bench model(Nagel, 2021; Keim \& Paulsen, 2019) have been observed.\\ 
It turns out that the response of many frustrated systems can be captured by an interacting collection of hysteretic two-state elements, called hysterons. The hysteron model, first suggested by Ferenc Preisach (Preisach, 1935), has long been used to model hysteretic systems as a collection of small hysteretic two-state elements. However, the Preisach model considers hysterons to be independent, while the interacting hysteron model has remained largely unexplored. The recent experimental findings show that the interacting hysteron model is relevant for many physical systems, and thus worth examining in more detail.\\
The possible metastable states and transitions between these states for a given hysteron system can be portrayed as a directed graph, which captures all possible responses of the system to driving (Regev, 2019). Numerical sampling work from our group has shown that the number of possible transition graphs for a system of interacting hysterons increases dramatically with the number of hysterons. For as few as three interacting hysterons, over 15,000 distinct graphs are found (Van Hecke, 2021). Because the number of possible transition graphs quickly grows overwhelming, a systematic method will be needed for categorizing the graphs.\\
Here we establish a systematic method to gradually approach the complexity of the interacting hysteron model, starting from the Preisach model. We first establish a formalism for constructing the transition graph for coupled hysterons by starting from a Preisach graph, and adding the effects of coupling step-by-step. We show how this formalism is used to construct a list of candidate graphs for a given number of hysterons. We then detail a method for checking whether a given transition graph can be realized, both in general and for a specific model. Finally, we illustrate our formalism for a model where hysterons are linearly coupled.\\
\section{Setup}
Here we detail the basic setup for simulating a system of $N$ hysterons. We define the state of the system $S$ as
\begin{equation}
    S = \{s_1, s_2, ..., s_N\}
\end{equation}
where $s_i \in \{0, 1\}$ are the phases of individual hysterons. We then model the response of individual hysterons to an external driving field $U$ by defining up and down switching fields $u_i^+$ and $u_i^-$. A hysteron transitions from phase 0 to 1 ('up') if $U \geq u_i^+$, and from phase 1 to 0 ('down') if $U \leq u_i^-$.\\
If the system of hysterons is non-interacting, then the switching fields $\{u_i^+\}, \{u_i^-\}$ are fixed values $u_i^{+, -}$. We refer to these switching fields in the absence of interactions as the bare switching fields. If there are interactions, the switching fields are modified by the state $S$:
\begin{equation}
    U_i^{+, -}(S) = U_i^{+, -} + \Delta u_i(S)
\end{equation}
 When a driving field $U$ is applied to a system with the collective state $S$, any hysterons that are in phase 0 and have $U \geq U_i^+$, or that are in phase 1 and have $U \leq U_i^-$, become unstable. If a single hysteron is unstable, that hysteron flips. If multiple hysterons are unstable, the system's response is ambiguous, as it is unclear which hysteron flips first and these operations do not commute if there is coupling. We therefore do not consider cases where multiple hysterons are unstable.\\
It can occur that the flipping of one hysteron destabilizes other hysterons when there is coupling. It may therefore take multiple iterations for the system to reach stability under a field $U$. We refer to this phenomenon as an avalanche. It is also possible that an avalanche leads back into the state itself, in which case the system becomes caught in a self-loop. We consider this scenario to be ill-defined, as the system's state is caught in an infinite loop.\\
The system's response to a field $U$ is thus obtained by comparing the field to the switching fields $\{U_i^+\}, \{U_i^-\}$ of the hysterons individually, flipping hysterons that are unstable, and repeating this process until there are no unstable hysterons. The response is ill-defined if multiple hysterons are unstable at the same time, or if the system becomes caught in an infinite self-loop.\\
The possible responses of a collection of $N$ hysterons to driving are captured by a state transition graph, which consists of all stable states $S$ and all transitions between these states. For a system of $N$ hysterons, there are $2^N$ possible states. In particular there are two saturated states, where either all $s_i=0$ or all $s_i=1$. Each state $S$ has a single up and down transition, except for the two saturated states, which only have an up and a down transition respectively. Therefore, a transition graph for a collection of $N$ hysterons consists of a maximum of $2^N$ states and $2(2^N-1)$ transitions.

\section{Topological approach}
In past work from our group, the possible transition graphs for two- and three-hysteron systems were found using numerical sampling. The obtained graphs contain several noteworthy phenomena that are not possible in the Preisach model, such as breaking of loop return point memory, scrambling, multiperiodic cycles and long transients (Van Hecke, 2021).\\
A significant disadvantage of numerical sampling is that it is not conclusive, as it is always possible that a region in parameter space leading to a certain transition graph is missed. Here we aim to establish a tool that can conclusively find all possible graphs for a given number of hysterons $N$.\\
Fortunately, it is not necessary to sample all of parameter space. The reason for this is that the transition graph for a given system does not depend on the absolute values of the switching fields $I_i^{+,-}(S)$, but only on the order of the switching fields. In principle, one could find all possible transition graphs for a given number of hysterons $N$ by evaluating all permutations of the order of the switching fields.\\
In practice, however, it is impractical to find the possible transition graphs by evaluating all possible orderings. This is because the transition graph only depends on a partial order of the switching fields, not on the total order, so that the number of permutations vastly outweighs the number of possible graphs.\\
Instead of evaluating all permutations of the total order of the switching fields, we find it more useful to take a reverse approach by starting from the topology. We first construct a number of candidate graphs, which describe the behaviour of a hysteron system in a well-defined way but are not necessarily realizable. We then generate a set of inequalities that the switching fields must obey so that the given candidate graph is obtained. Finally, we check whether the candidate graph can be realized by checking whether the generated set of inequalities has a solution. We thus obtain a list of possible graphs.\\
In addition to being an efficient method for conclusively finding the possible graphs, the method of candidate graphs also allows us to consider rational design of graphs. We can use the candidate graph method to directly consider the possibility of the interesting behaviours that have been observed previously, such as multiperiodic cycles and long transients, for a  given number of hysterons.\\
%We here explain our method for finding the possible graphs via candidate graphs. We first show how the design inequalities are obtained for a single graph. We explain how one can check if the set of inequalities has a solution using the well-established method of Fourier-Motzkin elimination. Secondly, we detail how one can construct a list of candidate graphs from all combinations of possible transition graphs. Finally, we improve on the candidate graphs method by establishing a notion of base graphs.
\section{Constructing graphs}\label{sec:constructing_graphs}
We here establish a method for finding the transition graphs that are possible for coupled hysterons. Rather than constructing the coupled transition graph from scratch, we start from a Preisach graph, then add the coupling effects of scrambling and avalanches one by one.\\
A well-defined transition graph for $N$ hysterons consists out of $2^N$ states, and $2(2^N-1)$ transitions, namely the up transitions for each state except the all-ones state and the down transitions for each state except the all-zero state. A transition graph is constructed by choosing a transition path for each of these $2(2^N-1)$ transitions. A transition path may be a single hysteron flip, or may consist of multiple flipped hysterons. When a transition path consists of multiple hysteron flips, we speak of an avalanche.\\
Naively, one can construct all possible transition graphs by finding the possible transition paths for each individual transition, and evaluating all possible combinations of transition paths. However, the naive method generates many transition graphs that are not solvable. For example, for $N=2$ one finds $3^5\times 6 = 1458$ graphs (Fig.\ref{fig:transition_paths_N2}), while the number of solvable graphs is only thirteen.\\
\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{possible_paths_v3.png}
    \caption{Overview of the possible transition paths for each $N=2$ transition individually. The greyed-out area signifies transitions that are left out when accounting for exchange symmetry.}
    \label{fig:transition_paths_N2}
\end{figure}
We can greatly reduce the number of candidate graphs by making a basic consideration about the allowed avalanches. We know that from a stable state $S$, hysteron $i$ can flip up if
\begin{equation}
    u_i^+(S) = \min_{s_j=0}u_j^+(S)
\end{equation}
and similarly, hysteron $i$ can flip down if
\begin{equation}
    u_i^-(S) = \max_{s_j=1}u_j^-(S)
\end{equation}
We now observe that, because we only consider the switching fields $u_i^{+,-}(S)$ to depend on the state $S$ and not on the driving field $U$, the same ordering must apply regardless of whether or not a state is initially stable. Thus, there is only ever one up and down transition from each state, even if the transition is only a part of a longer avalanche. As a result, one can construct the possible graphs more efficiently than in the naive method by first constructing all possible graphs consisting out of single hysteron flips ($l=1$), then evaluating the possible avalanches for each graph in turn. We refer to the graphs with only $l=1$ transitions as base graphs.\\
\begin{figure}[!h]
    \centering
    \includegraphics[width=0.5\textwidth]{breakdown_sketch.png}
    \caption{Breakdown of an example transition graph into a base graph and a combination of avalanches. The base graph can itself be separated into the main loop and a number of scrambled transitions.}
    \label{fig:basegraphs_avalanches}
\end{figure}\\
A caveat to the base graph argument is that, within an avalanche, it may be possible for multiple hysterons to become unstable at once. In addition, it is conceivable that the switching field for a real system depends not only on the state $S$ but also on the driving field $U$, since the physical state of the system is different for different values of $U$. We choose to confine ourselves to the part of design space where only one hysteron can become unstable at a time and the switching fields only depend on $S$, so that the the concept of base graphs holds.\\
It turns out that the idea of base graphs and avalanches provides us with a powerful framework for understanding the effects of hysteron interactions on the allowed transition graphs. \\
\subsection{Base graphs}
An advantage of the concept of base graphs is that, in the absence of avalanches, it is still relatively straightforward to count the number of possible graphs. We will now show how the number of base graphs increases in the presence of scrambling.\\
Scrambling entails that the ordering of switching fields can change throughout the graph. In order to discuss scrambling more explicitly, we here define the concept of the main loop of a transition graph. We define the up and down boundaries of the main loop as the series of up transitions going from the all-zero to the all-one state, and the series of down transitions going from the all-one to the all-zero state, respectively. In general, we account for exchange symmetry by fixing the ordering of the up boundary. Therefore, we often refer to the down boundary of the main loop as simply the main loop.\\
In the Preisach model, the ordering of the main loop fixes the transitions throughout the transition graph, so that each main loop corresponds to a unique Preisach graph. Because the down boundary of the main loop has $N!$ permutations, there are $N!$ Preisach graphs for a system of $N$ hysterons.\\
In a scrambled graph, one or more of the transitions in the graph deviates from the main loop. Therefore, when scrambling is allowed, there are multiple possible graphs for each main loop. We will now explicitly calculate the number of base graphs per main loop.\\
\begin{figure}[!h]
    \centering
    \includegraphics[width=0.5\textwidth]{basegraphs_counting_sketch.png}
    \caption{(a) Construction of possible base graphs from all combinations of $l=1$ transition graphs. (b) A pair of example graphs which are equal when garden-of-Eden states are ignored.}
    \label{fig:basegraphs_avalanches}
\end{figure}\\
To start with, we observe that the number of possible up and down flips for a state $S$ depends on the number of hysterons that is in phase 0 or 1. Defining the magnetisation of a state as
\begin{equation}
    M(S) = \sum_i s_i
\end{equation}
we can state that the number of possible up flips for a state $S$ is equal to $N-M(S)$, while the number of possible down flips is $M(S)$. To calculate the number of possible graphs, it makes sense to iterate over the magnetisation.\\
Next, we ask how many states exist with the magnetisation $M$. The number of states with the magnetisation $M$ is the number of possible binary numbers that has $M$ ones and $N-M$ zeros, which is equal to the binomial coefficient $\binom{N}{M}$.\\
It follows that the number of base graphs for a given number of hysterons $N$ is
\begin{equation}
    \#graphs = \left(\prod_{M=0}^{N}M^{\binom{N}{M}}\right)^2
\end{equation}
When the up boundary of the main loop is fixed to account for exchange symmetry, the number of base graphs is reduced by a factor $N!$. When the down boundary is also fixed so that the main loop is fixed, the number of base graphs is reduced by another factor $N!$. Thus, one obtains the number of base graphs per main loop:
\begin{equation}\label{eq:graph_count}
    \#graphs/ML = \frac{\left(\prod_{M=0}^{N}M^{\binom{N}{M}}\right)^2}{N!^2} = \left(\prod_{M=1}^{N-1}M^{\binom{N}{M}-1}\right)^2
\end{equation}
It should be noted that, when constructing the base graphs from all possible combinations of transitions, the resulting graphs often contain states that cannot be reached from the all-zero state. We refer to these states as garden-of-Eden states (Fig. \ref{fig:basegraphs_avalanches}b). We generally choose to ignore garden-of-Eden states. As a result, the base graphs as counted in Equation \ref{eq:graph_count} can contain duplicates, so that the true number of graphs turns out lower than this number. For example, for $N=3$, Equation \ref{eq:graph_count} gives that the number of base graphs is $6\times16=96$. When ignoring garden-of-Eden states, we find that the number of graphs is only 27.\\
\subsection{Avalanches}
\begin{figure}[!h]
    \centering
    \includegraphics[width=0.5\textwidth]{constructing_avalanches_sketch.png}
    \caption{Construction of an example $N=2$ graph by iteratively building up the avalanche $11\downarrow 10\downarrow 00$.}
    \label{fig:avalanches}
\end{figure}
We here show how the possible avalanches are evaluated for a given base graph.\\
We first note that we can build up avalanches iteratively. Namely, to have the $l=3$ avalanche $S^{(0)}\rightarrow S^{(1)} \rightarrow S^{(2)}$, one must at least have the $l=2$ avalanche $S^{(0)}\rightarrow S^{(1)}$. Thus, we start by evaluating all $l=2$ avalanches.\\
To have a possible avalanche $S^{(0)}\rightarrow S^{(1)} \rightarrow S^{(2)}$, there must be an incoming transition $S^{(0)}\rightarrow S^{(1)}$ at the state $S^{(1)}$, as well as an outcoming transition $S^{(1)} \rightarrow S^{(2)}$. Therefore, we can systematically find all possible $l=2$ avalanches in a base graph by constructing all combinations of incoming and outgoing transitions at each state. In addition, it must be checked for each avalanche that $S^{(0)} \neq S^{(2)}$, as an avalanche cannot revisit the same state.\\
Next, we consider how the avalanche length $l$ can be iterated over to obtain graphs with longer avalanches. In the previous step, we have explored all possible combinations of $l=2$ avalanches for the given base graph. To have an $l=3$ avalanche, an $l=2$ avalanche must be extended with an additional transition. Thus, similarly to our method for finding the $l=2$ avalanches, we find all $l=3$ avalanches for a given graph with only $l=2$ by evaluating all combinations of incoming $l=2$ and outgoing $l=1$ transitions at each state.\\
In summary, to construct all possible graphs for $N$ hysterons, we first construct all base graphs. We then generate the candidate graphs for each base graph by constructing the possible avalanches, and evaluating each combination of avalanches.\\
\section{Design inequalities}
We can efficiently construct a list of candidate graphs using the base graph method. However, not every generated graph is necessarily solvable. One can check whether a graph is solvable from the set of linear inequalities underlying the graph, which we refer to as the design inequalities.\\
We now consider in detail what the design inequalities of a graph look like, using an example $N=2$ graph (Fig. \ref{fig:design_ineqs_example}).\\
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{design_ineqs_sketch.png}
    \caption{Design inequalities for an example $N=2$ graph (a). Design inequalities are shown for (b) the $l=1$ transition $00\uparrow 01$ and (c) the $l=2$ avalanche $11\downarrow 10 \downarrow 00$.}
    \label{fig:design_ineqs_example}
\end{figure}\\
We first consider the inequalities required for the transition $00\uparrow 01$, which consists out of a single flip of hysteron 2. In order for hysteron 2 to flip before hysteron 1 when the driving $U$ is increased, one must have that $u_2^+(00) < u_1^+(01)$. Next, we must have that the state 01 is stable under the current driving, which is the switching field $u_2^+(00)$. The requirement for state 01 to be stable leads to two more inequalities, namely $u_1^+(01) > u_2^+(00)$ and $u_2^-(01) < u_2^+ (00)$.\\
As a second example, we consider the avalanche $11\downarrow 10 \downarrow 00$. Analogously to the previous example, we first require for hysteron 2 to be the first to flip down when decreasing the driving $U$, so that we obtain the inequality $u_2^-(11) > u_1^-(10)$. Next, a set of inequalities is required which describes the stability of the state 10 under the field $u_2^-(11)$. Unlike in the previous example, however, hysteron 1 must now be unstable. Thus, we obtain the set of inequalities $u_1^-(10) \geq u_2^-(11)$ and $u_2^+(10) > u_2^-(11)$\\
As described in Section \ref{sec:constructing_graphs}, the graph in Fig. \ref{fig:design_ineqs_example} can be broken down as the combination of a base graph and the avalanche $11\downarrow 10 \downarrow 00$. In the same way, we can distinguish two parts to the design inequalities. One one hand, for each transition there is a set of inequalities required to initiate the transition, which is of the form
\begin{equation}
    u_i^+(S^{(0)} = \min_{s_j = 0}u_j^+(S^{(0)})
\end{equation}
or 
\begin{equation}
    u_i-(S^{(0)} = \max_{s_j = 1}u_j^-(S^{(0)})
\end{equation}
The set of inequalities required to initiate the transition is associated with the base graph, and we refer to it accordingly as the base inequalities. On the other hand, for each transition there are $l$ sets of inequalities describing the stability of subsequent states under the field that initiated the transition. We refer to the part of the design inequalities that describes the stability as the relaxation inequalities.\\
For the general model where the switching fields $u_i^{+, -}(S)$ are independent, we note that the base inequalities are always solvable. This is because there is no overlap between the sets of inequalities for the individual transitions, since they describe relations between switching fields at the same state $S^{(0)}$. In contrast, the relaxation inequalities describe relations between switching fields at different states, so that it is possible for a combination of transitions to be incompatible even in the general model.\\
\section{Application to specific models}
We now illustrate how the base graph method is applied to the specific model where the coupling between hysterons is linear. Linear coupling entails that the switching fields $u_i^{+, -}(S)$ depend on the state $S$ as:
\begin{equation}
    u_i^{+, -}(S) = u_{i, 0}^{+, -} -\sum_{i \neq j}c_{ij}s_j
\end{equation}
Depending on the system, the allowed coupling coefficients $c_{ij}$ may be restricted. We consider two instances of the linear model for $N=3$. First, we look at the case where only one of the coupling coefficients $c_{ij}$ is unequal to zero. Second, we look at a model for hysterons in series, where the coupling is $c_{ij}  = c_j$ with all $c_j < 0$.\\
\subsection{Linear coupling}
\begin{figure}[!h]
    \centering
    \includegraphics[width=0.5\textwidth]{.png}
    \caption{Overview of possible scrambling and avalanches in the linear model for a single nonzero $c_ij$.}
    \label{fig:linear_coupling}
\end{figure}\\
\subsection{Hysterons in series}
\section{Discussion}
\section{Outlook}
\bibliography{apssamp}% Produces the bibliography via BibTeX.

\end{document}

### 2022-05-18 Paper_draft.tex
Changed title
Fixed float specifiers
Fixed notation of switching fields

@@
 
-\title{Methods for constructing the transition graphs of an interacting hysteron model}
+\title{Constructing the transition graphs of interacting hysterons}
 \author{Margot Teunisse}
@@
 \begin{equation}
-    U_i^{+, -}(S) = U_i^{+, -} + \Delta u_i(S)
+    U_i^{+, -}(S) = u_i^{+, -} + \Delta u_i(S)
 \end{equation}
@@
 Fortunately, it is not necessary to sample all of parameter space.
-The reason for this is that the transition graph for a given system does not depend on the absolute values of the switching fields $I_i^{+,-}(S)$, but only on the order of the switching fields.
+The reason for this is that the transition graph for a given system does not depend on the absolute values of the switching fields $U_i^{+,-}(S)$, but only on the order of the switching fields.
 In principle, one could find all possible transition graphs for a given number of hysterons $N$ by evaluating all permutations of the order of the switching fields.\\
@@
 \begin{equation}
-    u_i^+(S) = \min_{s_j=0}u_j^+(S)
+    U_i^+(S) = \min_{s_j=0}U_j^+(S)
 \end{equation}
@@
 \begin{equation}
-    u_i^-(S) = \max_{s_j=1}u_j^-(S)
+    U_i^-(S) = \max_{s_j=1}U_j^-(S)
 \end{equation}
-We now observe that, because we only consider the switching fields $u_i^{+,-}(S)$ to depend on the state $S$ and not on the driving field $U$, the same ordering must apply regardless of whether or not a state is initially stable.
+We now observe that, because we only consider the switching fields $U_i^{+,-}(S)$ to depend on the state $S$ and not on the driving field $U$, the same ordering must apply regardless of whether or not a state is initially stable.
 Thus, there is only ever one up and down transition from each state, even if the transition is only a part of a longer avalanche.
@@
 We refer to the graphs with only $l=1$ transitions as base graphs.\\
-\begin{figure}[!h]
+\begin{figure}[!ht]
     \centering
@@
 We will now explicitly calculate the number of base graphs per main loop.\\
-\begin{figure}[!h]
+\begin{figure}[!ht]
     \centering
@@
 \subsection{Avalanches}
-\begin{figure}[!h]
+\begin{figure}[!ht]
     \centering
@@
 We now consider in detail what the design inequalities of a graph look like, using an example $N=2$ graph (Fig. \ref{fig:design_ineqs_example}).\\
-\begin{figure}[h!]
+\begin{figure}[ht!]
     \centering
@@
 We first consider the inequalities required for the transition $00\uparrow 01$, which consists out of a single flip of hysteron 2.
-In order for hysteron 2 to flip before hysteron 1 when the driving $U$ is increased, one must have that $u_2^+(00) < u_1^+(01)$.
-Next, we must have that the state 01 is stable under the current driving, which is the switching field $u_2^+(00)$.
-The requirement for state 01 to be stable leads to two more inequalities, namely $u_1^+(01) > u_2^+(00)$ and $u_2^-(01) < u_2^+ (00)$.\\
+In order for hysteron 2 to flip before hysteron 1 when the driving $U$ is increased, one must have that $U_2^+(00) < U_1^+(01)$.
+Next, we must have that the state 01 is stable under the current driving, which is the switching field $U_2^+(00)$.
+The requirement for state 01 to be stable leads to two more inequalities, namely $U_1^+(01) > U_2^+(00)$ and $U_2^-(01) < U_2^+ (00)$.\\
 As a second example, we consider the avalanche $11\downarrow 10 \downarrow 00$.
-Analogously to the previous example, we first require for hysteron 2 to be the first to flip down when decreasing the driving $U$, so that we obtain the inequality $u_2^-(11) > u_1^-(10)$.
-Next, a set of inequalities is required which describes the stability of the state 10 under the field $u_2^-(11)$.
+Analogously to the previous example, we first require for hysteron 2 to be the first to flip down when decreasing the driving $U$, so that we obtain the inequality $U_2^-(11) > U_1^-(10)$.
+Next, a set of inequalities is required which describes the stability of the state 10 under the field $U_2^-(11)$.
 Unlike in the previous example, however, hysteron 1 must now be unstable.
-Thus, we obtain the set of inequalities $u_1^-(10) \geq u_2^-(11)$ and $u_2^+(10) > u_2^-(11)$\\
+Thus, we obtain the set of inequalities $U_1^-(10) \geq U_2^-(11)$ and $U_2^+(10) > U_2^-(11)$\\
 As described in Section \ref{sec:constructing_graphs}, the graph in Fig.
@@
 \begin{equation}
-    u_i^+(S^{(0)} = \min_{s_j = 0}u_j^+(S^{(0)})
+    U_i^+(S^{(0)} = \min_{s_j = 0}U_j^+(S^{(0)})
 \end{equation}
@@
 \begin{equation}
-    u_i-(S^{(0)} = \max_{s_j = 1}u_j^-(S^{(0)})
+    U_i-(S^{(0)} = \max_{s_j = 1}U_j^-(S^{(0)})
 \end{equation}
@@
 We now illustrate how the base graph method is applied to the specific model where the coupling between hysterons is linear.
-Linear coupling entails that the switching fields $u_i^{+, -}(S)$ depend on the state $S$ as:
+Linear coupling entails that the switching fields $U_i^{+, -}(S)$ depend on the state $S$ as:
 \begin{equation}
-    u_i^{+, -}(S) = u_{i, 0}^{+, -} -\sum_{i \neq j}c_{ij}s_j
+    U_i^{+, -}(S) = u_i^{+, -} -\sum_{i \neq j}c_{ij}s_j
 \end{equation}
@@
 \subsection{Linear coupling}
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=0.5\textwidth]{.png}
-    \caption{Overview of possible scrambling and avalanches in the linear model for a single nonzero $c_ij$.}
-    \label{fig:linear_coupling}
-\end{figure}\\
+%\begin{figure}[!ht]
+%    \centering
+%    \includegraphics[width=0.5\textwidth]{.png}
+%    \caption{Overview of possible scrambling and avalanches in the linear model for a single nonzero $c_ij$.}
+%    \label{fig:linear_coupling}
+%\end{figure}\\
 \subsection{Hysterons in series}
@@
 \section{Outlook}
-\bibliography{apssamp}% Produces the bibliography via BibTeX.
+%\bibliography{apssamp}% Produces the bibliography via BibTeX.
 

### 2022-05-18 Paper_draft.tex
Removed caveat to base graph argument

@@
     \label{fig:basegraphs_avalanches}
-\end{figure}\\
-A caveat to the base graph argument is that, within an avalanche, it may be possible for multiple hysterons to become unstable at once.
-In addition, it is conceivable that the switching field for a real system depends not only on the state $S$ but also on the driving field $U$, since the physical state of the system is different for different values of $U$.
-We choose to confine ourselves to the part of design space where only one hysteron can become unstable at a time and the switching fields only depend on $S$, so that the the concept of base graphs holds.\\
+\end{figure}
 It turns out that the idea of base graphs and avalanches provides us with a powerful framework for understanding the effects of hysteron interactions on the allowed transition graphs. \\

### 2022-05-18 Paper_draft.tex
Corrected instance where l was not explicitly referred to as transition length & changed notation from all-zero/all-one state to saturated states. Note that down boundary of main loop is now not defined.

@@
 Thus, there is only ever one up and down transition from each state, even if the transition is only a part of a longer avalanche.
-As a result, one can construct the possible graphs more efficiently than in the naive method by first constructing all possible graphs consisting out of single hysteron flips ($l=1$), then evaluating the possible avalanches for each graph in turn.
+As a result, one can construct the possible graphs more efficiently than in the naive method by first constructing all possible graphs consisting out of single hysteron flips (i.e., transitions with transition length $l=1$), then evaluating the possible avalanches for each graph in turn.
 We refer to the graphs with only $l=1$ transitions as base graphs.\\

### 2022-05-25 45thgraph.tex
Added separate text about 45th series graph

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}

\begin{document}

\section{The 45th series graph}
For three hysterons in series, we have obtained 44 realizable graphs, assuming a model where $c_{ij}=c_j, c_j \leq 0$.  We construct the graphs using the base graph method, where we first construct all possible 
\begin{enumerate}
    \item When $c_{ij}=c_j$, there is no scrambling, so the only base graphs are the Preisach graphs.
    \item When $c_{j} \leq $, there can only be antiferromagnetic avalanches,
    \item As a result of restrictions 1 and 2, there can only be avalanches of length $l=2$.
    \item When $c_{ij} = c_j$ svalanches involving the same hysteron flips in the same directions must occur together. 
\end{enumerate}
After applying the restrictions, there are 45 candidate graphs for three hysterons in series. We find that 44 of these graphs are realizable, while a single graph is not (Fig. \ref{fig:45thgraph}. We now ask why the 45th graph is not realizable.
\begin{figure}[!ht]
    \centering
    \includegraphics[width=0.8\textwidth]{45thgraph.png}
    \caption{The single impossible candidate graph for three hysterons in series.}
    \label{fig:45thgraph}
\end{figure}\\
A graph is realizable if the underlying set of design inequalities has a solution. We reason that all four transitions $001\uparrow 011$, $011\uparrow111\downarrow110$, $110\downarrow 010$ and $010\downarrow000\uparrow 001$ must be involved in the combination of inequalities that is incompatible, since more than one of the candidate graphs would otherwise be impossible.\\
To know whether a set of inequalities is solvable, one can use the Fourier-Motzkin method for elimination of variables. In the Fourier-Motzkin method, a variable $x$ is eliminated by combining the inequalities to create a new set that does not contain $x$. A set of inequalities does not have a solution if, after all variables are eliminated, a contradictory statement remains such as $0 > 0$. By working backwards, we can identify which combinations of inequalities lead to a contradictory statement and are therefore incompatible.\\
We find that for the 45th graph, there is a single combination of six inequalities that is incompatible, namely:
\begin{equation}
\begin{split}
    u_1^- - c_2 &> u_2^- - c_1\\
    u_3^+ &> u_1^-\\
    u_2^- &\geq u_3^+\\
    u_2^+ - c_3 &> u_3^- - c_2\\
    u_1^+ &> u_2^+\\
    u_3^- - c_1 &\geq u_1^+ - c_3\\
\end{split}
\end{equation}
We further note that the six inequalities arise from the four transitions $001\uparrow 011$, $011\uparrow111\downarrow110$, $110\downarrow 010$ and $010\downarrow000\uparrow 001$ (Fig. \ref{fig:culprit_transitions}), in agreement with our prediction.
\begin{figure}[!ht]
    \centering
    \includegraphics[width=0.8\textwidth]{45thgraph_culprit_withineqs.png}
    \caption{The four transitions of the 45th graph that are not compatible: $001\uparrow 011$, $011\uparrow111\downarrow110$, $110\downarrow 010$ and $010\downarrow000\uparrow 001$.}
    \label{fig:culprit_transitions}
\end{figure}\\
The 45th graph thus illustrates that it is not trivial to see whether a combination of transitions of compatible, and that it therefore remains necessary to explicitly check whether candidate graphs are solvable by generating the design inequalities.

\end{document}

### 2022-05-25 Paper_draft.tex
Added figure for N=2 and N=3 base graphs

@@
 We refer to the graphs with only $l=1$ transitions as base graphs.\\
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{base_graphs.png}
+    \caption{All possible base graphs for the two- and three-hysteron systems.
+a) All base graphs for $N=2$; since scrambling is not possible for $N=2$, the base graphs are the two Preisach graphs.
+b) Preisach graphs for $N=3$.
+c) Scrambled base graphs for N=3 that are possible for linear coupling.}
+    \label{fig:basegraphs_n3}
+\end{figure}
 \begin{figure}[!ht]
@@
 Scrambling entails that the ordering of switching fields can change throughout the graph.
-In order to discuss scrambling more explicitly, we here define the concept of the main loop of a transition graph.
-We define the up and down boundaries of the main loop as the series of up transitions going from the all-zero to the all-one state, and the series of down transitions going from the all-one to the all-zero state, respectively.
-In general, we account for exchange symmetry by fixing the ordering of the up boundary.
-Therefore, we often refer to the down boundary of the main loop as simply the main loop.\\
+In order to discuss scrambling more explicitly, we here define the main loop as the series of up and down transitions connecting the two saturated states.
 In the Preisach model, the ordering of the main loop fixes the transitions throughout the transition graph, so that each main loop corresponds to a unique Preisach graph.

### 2022-05-25 Paper_draft.tex
Added figure showing examples of impossible combinations of transitions

@@
     \centering
+    \includegraphics[width=0.5\textwidth]{impossible_graphs.png}
+    \caption{Examples of impossible combinations of transitions for the two-hysteron system.
+a) Several examples of impossible combinations of transitions.
+b) Example of an combination of transitions that is impossible due to a violation of the underlying base graph.
+c) Illustration of how the graph in (b) violates the underlying base graph.}
+    \label{fig:impossiblegraphs}
+\end{figure}
+\begin{figure}
+    \centering
     \includegraphics[width=0.5\textwidth]{base_graphs.png}

### 2022-05-25 Paper_draft.tex
Reworked part about impossible subgraphs & base graph argument

@@
 Naively, one can construct all possible transition graphs by finding the possible transition paths for each individual transition, and evaluating all possible combinations of transition paths.
-However, the naive method generates many transition graphs that are not solvable.
-For example, for $N=2$ one finds $3^5\times 6 = 1458$ graphs (Fig.\ref{fig:transition_paths_N2}), while the number of solvable graphs is only thirteen.\\
+However, the naive method generates many transition graphs that are not realizable.
+For example, for $N=2$ one finds $3^5\times 6 = 1458$ graphs (Fig.\ref{fig:transition_paths_N2}), while the number of solvable graphs is only thirteen for linear coupling.\\
 \begin{figure}
@@
 \end{figure}
-We can greatly reduce the number of candidate graphs by making a basic consideration about the allowed avalanches. We know that from a stable state $S$, hysteron $i$ can flip up if
-\begin{equation}
-    U_i^+(S) = \min_{s_j=0}U_j^+(S)
-\end{equation}
-and similarly, hysteron $i$ can flip down if
-\begin{equation}
-    U_i^-(S) = \max_{s_j=1}U_j^-(S)
-\end{equation}
-We now observe that, because we only consider the switching fields $U_i^{+,-}(S)$ to depend on the state $S$ and not on the driving field $U$, the same ordering must apply regardless of whether or not a state is initially stable.
-Thus, there is only ever one up and down transition from each state, even if the transition is only a part of a longer avalanche.
-As a result, one can construct the possible graphs more efficiently than in the naive method by first constructing all possible graphs consisting out of single hysteron flips (i.e., transitions with transition length $l=1$), then evaluating the possible avalanches for each graph in turn.
-We refer to the graphs with only $l=1$ transitions as base graphs.\\
+To better understand why some graphs are not realizable,  we look in detail at the design inequalities underlying the graphs (see SI), and identify the inequalities that are in conflict with one another.
+By then tracing these inequalities back to the transitions from which we arise, we find the combinations of transitions (i.e., subgraphs) that are incompatible and thus make a graph not realizable.
+Several examples of impossible subgraphs are given in Fig.
+\ref{fig:impossiblegraphs}a.\\
+We now direct our attention to a particular group of impossible subgraphs, an example of which is shown in Fig.
+\ref{fig:impossiblegraphs}b.
+The example subgraph consists of the single-flip transition $11\downarrow 10$, and the avalanche $10\uparrow 11 \downarrow 01$.
+We observe that the transition $11 \downarrow 10$ requires that $U_2^-(11) > U_1^-(11)$ to have hysteron 2 flip down from the state 11.
+Conversely, the transition $10\uparrow 11 \downarrow 01$ requires the inequality $U_1^-(11) > U_2^-(11)$ to have an avalanche where only hysteron 1 flips down from the state 11.
+The contradiction between the two transitions arises because the avalanche $10 \uparrow 11 \downarrow 01$ imposes that the switching field $U_1^-$ is the highest down switching field, even though the transition $11 \downarrow 01$ is only a part of a larger avalanche.\\
+The argument used for the example subgraph can be extended to the general argument that the up and down flips which can occur from a state do not depend on whether or not that state is stable.
+As a consequence, all avalanches occuring in a graph must conform to an underlying graph of single-flip transitions, which we refer to as the base graph.
+\\
+The idea of base graphs allows us to improve our method for generating candidate graphs.
+Namely, by first constructing all base graphs, and only then evaluating all possible avalanches for each base graph individually, we exclude the subgraphs of the type shown in Fig.
+\ref{fig:impossiblegraphs}b from the outset.
+Because the number of graphs for which the design inequalities need to be explicitly generated is then reduced, the base graph method has an improved efficiency compared to the naive approach.
 \begin{figure}
@@
 b) Example of an combination of transitions that is impossible due to a violation of the underlying base graph.
-c) Illustration of how the graph in (b) violates the underlying base graph.}
+c) Illustration of how the combination of transitions in (b) violates the underlying base graph.}
     \label{fig:impossiblegraphs}
@@
 \end{figure}
-It turns out that the idea of base graphs and avalanches provides us with a powerful framework for understanding the effects of hysteron interactions on the allowed transition graphs. \\
+In addition to the base graph method being an efficient method for generating candidate graphs, it also providedes us with a powerful framework for understanding the effects of hysteron interactions on the allowed transition graphs.
+\\
 \subsection{Base graphs}

### 2022-05-30 Paper_draft.tex
Changed structure for section about constructing graphs
Added figure sketch for exchange symmetry & garden-of-Eden states
Removed figure sketch for base graph counting
Added piece about exchange symmetry

@@
 We can use the candidate graph method to directly consider the possibility of the interesting behaviours that have been observed previously, such as multiperiodic cycles and long transients, for a  given number of hysterons.\\
-%We here explain our method for finding the possible graphs via candidate graphs.
-We first show how the design inequalities are obtained for a single graph.
-We explain how one can check if the set of inequalities has a solution using the well-established method of Fourier-Motzkin elimination.
-Secondly, we detail how one can construct a list of candidate graphs from all combinations of possible transition graphs.
-Finally, we improve on the candidate graphs method by establishing a notion of base graphs.
 \section{Constructing graphs}\label{sec:constructing_graphs}
@@
 Rather than constructing the coupled transition graph from scratch, we start from a Preisach graph, then add the coupling effects of scrambling and avalanches one by one.\\
+\subsection{Candidate graphs}
 A well-defined transition graph for $N$ hysterons consists out of $2^N$ states, and $2(2^N-1)$ transitions, namely the up transitions for each state except the all-ones state and the down transitions for each state except the all-zero state.
@@
 For example, for $N=2$ one finds $3^5\times 6 = 1458$ graphs (Fig.\ref{fig:transition_paths_N2}), while the number of solvable graphs is only thirteen for linear coupling.\\
-\begin{figure}
+\begin{figure}[ht!]
     \centering
@@
 \end{figure}
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.5\textwidth]{exchange_plus_goe.png}
+    \caption{Considerations for removing duplicate graphs: a) exchange symmetry and b) garden-of-Eden states.}
+    \label{fig:exchangeplusgoe}
+\end{figure}
+\subsubsection{Exchange symmetry}
+The hysterons in our model are considered as indistinguishable particles.
+That is, when we define the state $S = \{s_1, s_2, ..., s_N\}$, the labelling of hysterons 1 through N is arbitrary.
+As a result, when two graphs only differ from one another by the ordering of the hysterons 1, 2, ..., N, we consider the graphs to be the same (Fig.
+\ref{fig:exchangeplusgoe}a).\\
+To account for exchange symmetry, we fix the order in which hysterons 1, 2, ..., N flip up when increasing the external field from the ground state.
+For example, for $N=3$, we have that hysteron 3 flips up first from the state 000, hysteron 2 flips up first from 001, and trivially hysteron 1 flips up first from 011.
+Since there are $N!$ permutations of the order of $N$ hysterons, accounting for exchange symmetry decreases the number of candidate graphs by a factor $N!$.
+\subsubsection{Garden-of-Eden states}
+\subsection{Realizability}
 To better understand why some graphs are not realizable,  we look in detail at the design inequalities underlying the graphs (see SI), and identify the inequalities that are in conflict with one another.
@@
 \end{figure}
+In addition to the base graph method being an efficient method for generating candidate graphs, it also providedes us with a powerful framework for understanding the effects of hysteron interactions on the allowed transition graphs.
+\\
+\subsection{The base graph method}
 \begin{figure}[!ht]
@@
 \end{figure}
-In addition to the base graph method being an efficient method for generating candidate graphs, it also providedes us with a powerful framework for understanding the effects of hysteron interactions on the allowed transition graphs.
-\\
-\subsection{Base graphs}
+\subsubsection{Base graphs}
 An advantage of the concept of base graphs is that, in the absence of avalanches, it is still relatively straightforward to count the number of possible graphs.
@@
 We will now explicitly calculate the number of base graphs per main loop.\\
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=0.5\textwidth]{basegraphs_counting_sketch.png}
-    \caption{(a) Construction of possible base graphs from all combinations of $l=1$ transition graphs. (b) A pair of example graphs which are equal when garden-of-Eden states are ignored.}
-    \label{fig:basegraphs_avalanches}
-\end{figure}\\
 To start with, we observe that the number of possible up and down flips for a state $S$ depends on the number of hysterons that is in phase 0 or 1. Defining the magnetisation of a state as
@@
 When ignoring garden-of-Eden states, we find that the number of graphs is only 27.\\
-\subsection{Avalanches}
+\subsubsection{Avalanches}
 \begin{figure}[!ht]

### 2022-05-30 Paper_draft.tex
Added piece about garden-of-Eden states

@@
 \subsubsection{Garden-of-Eden states}
+It often occurs that one or more of the possible states for $N$ hysterons cannot be reached from the ground state.
+We refer to such states which cannot be reached as garden-of-Eden states.
+Because the transitions from garden-of-Eden states are irrelevant when one starts from the ground state, as is generally the case in our experiments, we may choose to ignore garden-of-Eden states.
+As a consequence, when two graphs only differ from one another by transitions that occur from garden-of-Eden states, the graphs become duplicates.
+Thus, when garden-of-Eden states are ignored, the number of distinct graphs can turn out lower than the number of possible combinations of transitions.
 \subsection{Realizability}

### 2022-05-30 Paper_draft.tex
Reworked intro for piece on candidate graphs & added explicit numbers for effect of exchange symmetry/garden-of-Eden states

@@
 When a transition path consists of multiple hysteron flips, we speak of an avalanche.\\
-Naively, one can construct all possible transition graphs by finding the possible transition paths for each individual transition, and evaluating all possible combinations of transition paths.
-However, the naive method generates many transition graphs that are not realizable.
-For example, for $N=2$ one finds $3^5\times 6 = 1458$ graphs (Fig.\ref{fig:transition_paths_N2}), while the number of solvable graphs is only thirteen for linear coupling.\\
+Naively, one can construct all possible transition graphs by finding the possible transition paths for each individual transition.
+For example, for $N=2$ one finds $3^4\times 6^2 = 2916$ graphs (Fig.\ref{fig:transition_paths_N2}).
+We will now make two considerations that reduce the number of candidate graphs, namely exchange symmetry and garden-of-Eden states.
 \begin{figure}[ht!]
@@
 Since there are $N!$ permutations of the order of $N$ hysterons, accounting for exchange symmetry decreases the number of candidate graphs by a factor $N!$.
+Thus, for $N=2$, the number of candidate graphs is reduced by a factor 2 from 2916 to 1458.
 \subsubsection{Garden-of-Eden states}
@@
 As a consequence, when two graphs only differ from one another by transitions that occur from garden-of-Eden states, the graphs become duplicates.
-Thus, when garden-of-Eden states are ignored, the number of distinct graphs can turn out lower than the number of possible combinations of transitions.
+Therefore, when garden-of-Eden states are ignored, the number of distinct graphs can turn out lower than the number of possible combinations of transitions.
+For $N=2$, ignoring garden-of-Eden states  reduces the number of graphs from 1458 to 752.
 \subsection{Realizability}

### 2022-05-30 Paper_draft.tex
Reworked introduction to section on constructing graphs

@@
 We here establish a method for finding the transition graphs that are possible for coupled hysterons.
-Rather than constructing the coupled transition graph from scratch, we start from a Preisach graph, then add the coupling effects of scrambling and avalanches one by one.\\
-\subsection{Candidate graphs}
+We first discuss in section \ref{ssec:candidate_graphs} how one can generate a list of candidate graphs that includes all possible graphs for a given number of hysterons $N$.
+Next, in section \ref{ssec:realizability}, we explain how to evaluate whether or not a graph is realizable by checking whether its underlying design inequalities have a solution.
+Finally, we improve on the candidate graph method by introducing the concept of base graphs.
+\subsection{Candidate graphs}\label{ssec:candidate_graphs}
 A well-defined transition graph for $N$ hysterons consists out of $2^N$ states, and $2(2^N-1)$ transitions, namely the up transitions for each state except the all-ones state and the down transitions for each state except the all-zero state.
@@
 For $N=2$, ignoring garden-of-Eden states  reduces the number of graphs from 1458 to 752.
-\subsection{Realizability}
+\subsection{Realizability}\label{ssec:realizability}
 To better understand why some graphs are not realizable,  we look in detail at the design inequalities underlying the graphs (see SI), and identify the inequalities that are in conflict with one another.

### 2022-05-30 Paper_draft.tex
Reworked piece on garden-of-Eden states for base graphs to reflect added piece in candidate graphs section

@@
 \end{equation}
-It should be noted that, when constructing the base graphs from all possible combinations of transitions, the resulting graphs often contain states that cannot be reached from the all-zero state.
-We refer to these states as garden-of-Eden states (Fig.
-\ref{fig:basegraphs_avalanches}b).
-We generally choose to ignore garden-of-Eden states.
-As a result, the base graphs as counted in Equation \ref{eq:graph_count} can contain duplicates, so that the true number of graphs turns out lower than this number.
-For example, for $N=3$, Equation \ref{eq:graph_count} gives that the number of base graphs is $6\times16=96$.
-When ignoring garden-of-Eden states, we find that the number of graphs is only 27.\\
+The number of graphs given by Equation \label{eq:graph_count} takes into account exchange symmetry, but not garden-of-Eden states (Section \ref{ssec:candidate_graphs}), and thus gives a maximum on the number of base graphs.
+For example, for $N=3$, the number of base graphs provided by Equation \ref{eq:graph_count} is 96, while ignoring garden-of-Eden states reduces the number of base graphs to 35 (Fig.
+\ref{fig:basegraphs_n3}).
 \subsubsection{Avalanches}

### 2022-05-31 Paper_draft.tex
Moved piece about design inequalities to SI

@@
 We then generate the candidate graphs for each base graph by constructing the possible avalanches, and evaluating each combination of avalanches.\\
-\section{Design inequalities}
-We can efficiently construct a list of candidate graphs using the base graph method.
-However, not every generated graph is necessarily solvable.
-One can check whether a graph is solvable from the set of linear inequalities underlying the graph, which we refer to as the design inequalities.\\
-We now consider in detail what the design inequalities of a graph look like, using an example $N=2$ graph (Fig. \ref{fig:design_ineqs_example}).\\
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=0.5\textwidth]{design_ineqs_sketch.png}
-    \caption{Design inequalities for an example $N=2$ graph (a).
-Design inequalities are shown for (b) the $l=1$ transition $00\uparrow 01$ and (c) the $l=2$ avalanche $11\downarrow 10 \downarrow 00$.}
-    \label{fig:design_ineqs_example}
-\end{figure}\\
-We first consider the inequalities required for the transition $00\uparrow 01$, which consists out of a single flip of hysteron 2.
-In order for hysteron 2 to flip before hysteron 1 when the driving $U$ is increased, one must have that $U_2^+(00) < U_1^+(01)$.
-Next, we must have that the state 01 is stable under the current driving, which is the switching field $U_2^+(00)$.
-The requirement for state 01 to be stable leads to two more inequalities, namely $U_1^+(01) > U_2^+(00)$ and $U_2^-(01) < U_2^+ (00)$.\\
-As a second example, we consider the avalanche $11\downarrow 10 \downarrow 00$.
-Analogously to the previous example, we first require for hysteron 2 to be the first to flip down when decreasing the driving $U$, so that we obtain the inequality $U_2^-(11) > U_1^-(10)$.
-Next, a set of inequalities is required which describes the stability of the state 10 under the field $U_2^-(11)$.
-Unlike in the previous example, however, hysteron 1 must now be unstable.
-Thus, we obtain the set of inequalities $U_1^-(10) \geq U_2^-(11)$ and $U_2^+(10) > U_2^-(11)$\\
-As described in Section \ref{sec:constructing_graphs}, the graph in Fig.
-\ref{fig:design_ineqs_example} can be broken down as the combination of a base graph and the avalanche $11\downarrow 10 \downarrow 00$.
-In the same way, we can distinguish two parts to the design inequalities.
-One one hand, for each transition there is a set of inequalities required to initiate the transition, which is of the form
-\begin{equation}
-    U_i^+(S^{(0)} = \min_{s_j = 0}U_j^+(S^{(0)})
-\end{equation}
-or 
-\begin{equation}
-    U_i-(S^{(0)} = \max_{s_j = 1}U_j^-(S^{(0)})
-\end{equation}
-The set of inequalities required to initiate the transition is associated with the base graph, and we refer to it accordingly as the base inequalities.
-On the other hand, for each transition there are $l$ sets of inequalities describing the stability of subsequent states under the field that initiated the transition.
-We refer to the part of the design inequalities that describes the stability as the relaxation inequalities.\\
-For the general model where the switching fields $u_i^{+, -}(S)$ are independent, we note that the base inequalities are always solvable.
-This is because there is no overlap between the sets of inequalities for the individual transitions, since they describe relations between switching fields at the same state $S^{(0)}$.
-In contrast, the relaxation inequalities describe relations between switching fields at different states, so that it is possible for a combination of transitions to be incompatible even in the general model.\\
 \section{Application to specific models}

### 2022-05-31 SI_design_ineqs.tex
Moved piece about design inequalities to SI

\documentclass{article}

\usepackage{graphicx}
\usepackage{amsmath}

\begin{document}

\section{Design inequalities}
We can efficiently construct a list of candidate graphs using the base graph method. However, not every generated graph is necessarily solvable. One can check whether a graph is solvable from the set of linear inequalities underlying the graph, which we refer to as the design inequalities.\\
We now consider in detail what the design inequalities of a graph look like, using an example $N=2$ graph (Fig. \ref{fig:design_ineqs_example}).\\
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{design_ineqs_sketch.png}
    \caption{Design inequalities for an example $N=2$ graph (a). Design inequalities are shown for (b) the $l=1$ transition $00\uparrow 01$ and (c) the $l=2$ avalanche $11\downarrow 10 \downarrow 00$.}
    \label{fig:design_ineqs_example}
\end{figure}\\
We first consider the inequalities required for the transition $00\uparrow 01$, which consists out of a single flip of hysteron 2. In order for hysteron 2 to flip before hysteron 1 when the driving $U$ is increased, one must have that $U_2^+(00) < U_1^+(01)$. Next, we must have that the state 01 is stable under the current driving, which is the switching field $U_2^+(00)$. The requirement for state 01 to be stable leads to two more inequalities, namely $U_1^+(01) > U_2^+(00)$ and $U_2^-(01) < U_2^+ (00)$.\\
As a second example, we consider the avalanche $11\downarrow 10 \downarrow 00$. Analogously to the previous example, we first require for hysteron 2 to be the first to flip down when decreasing the driving $U$, so that we obtain the inequality $U_2^-(11) > U_1^-(10)$. Next, a set of inequalities is required which describes the stability of the state 10 under the field $U_2^-(11)$. Unlike in the previous example, however, hysteron 1 must now be unstable. Thus, we obtain the set of inequalities $U_1^-(10) \geq U_2^-(11)$ and $U_2^+(10) > U_2^-(11)$\\
As described in Section \ref{sec:constructing_graphs}, the graph in Fig. \ref{fig:design_ineqs_example} can be broken down as the combination of a base graph and the avalanche $11\downarrow 10 \downarrow 00$. In the same way, we can distinguish two parts to the design inequalities. One one hand, for each transition there is a set of inequalities required to initiate the transition, which is of the form
\begin{equation}
    U_i^+(S^{(0)} = \min_{s_j = 0}U_j^+(S^{(0)})
\end{equation}
or 
\begin{equation}
    U_i-(S^{(0)} = \max_{s_j = 1}U_j^-(S^{(0)})
\end{equation}
The set of inequalities required to initiate the transition is associated with the base graph, and we refer to it accordingly as the base inequalities. On the other hand, for each transition there are $l$ sets of inequalities describing the stability of subsequent states under the field that initiated the transition. We refer to the part of the design inequalities that describes the stability as the relaxation inequalities.\\
For the general model where the switching fields $u_i^{+, -}(S)$ are independent, we note that the base inequalities are always solvable. This is because there is no overlap between the sets of inequalities for the individual transitions, since they describe relations between switching fields at the same state $S^{(0)}$. In contrast, the relaxation inequalities describe relations between switching fields at different states, so that it is possible for a combination of transitions to be incompatible even in the general model.\\

\end{document}

### 2022-05-31 SI_design_ineqs.tex
Added definitions for U_i(S) and r_i to help notation

@@
 One can check whether a graph is solvable from the set of linear inequalities underlying the graph, which we refer to as the design inequalities.\\
+We recall that a hysteron $i$ is stable under an external field $U$ if:
+\begin{equation}\label{eq:dynamics}
+\begin{cases}
+    U &>  U_i^+(S), s_i=0\\
+    U &< U_i^-(S), s_i=1\\
+\end{cases}
+\end{equation}
+To help our notation, we here define that
+\begin{equation}
+U_i(S) = 
+\begin{cases}
+    U_i^+(S), s_i=0\\
+     U_i^-(S), s_i=1\\
+\end{cases}
+\end{equation}
+We also define the direction $r_i$ as:
+\begin{equation}
+r_i = 1-2s_i
+\end{equation}
+so that $r_i = 1$ if $s_i=0$ and $r_i=-1$ if $s_i=1$.\\
+We can then rewrite the conditions from Equation \ref{eq:dynamics} into a single statement: 
+\begin{equation}
+ r_iU_i(S) > r_iU
+\end{equation}
 We now consider in detail what the design inequalities of a graph look like, using an example $N=2$ graph (Fig. \ref{fig:design_ineqs_example}).\\

### 2022-05-31 SI_design_ineqs.tex
Reworked piece on design inequalities using new definitions

@@
 so that $r_i = 1$ if $s_i=0$ and $r_i=-1$ if $s_i=1$.\\
-We can then rewrite the conditions from Equation \ref{eq:dynamics} into a single statement: 
+We can then rewrite the conditional statement from Equation \ref{eq:dynamics} into a single statement: 
 \begin{equation}
@@
 Thus, we obtain the set of inequalities $U_1^-(10) \geq U_2^-(11)$ and $U_2^+(10) > U_2^-(11)$\\
-As described in Section \ref{sec:constructing_graphs}, the graph in Fig.
-\ref{fig:design_ineqs_example} can be broken down as the combination of a base graph and the avalanche $11\downarrow 10 \downarrow 00$.
-In the same way, we can distinguish two parts to the design inequalities.
+We can generalize the method for finding the design inequalities to any transition path $S^{(0)}\rightarrow S^{(1)}\rightarrow ...
+\rightarrow S^{(1)}$.
 One one hand, for each transition there is a set of inequalities required to initiate the transition, which is of the form
 \begin{equation}
-    U_i^+(S^{(0)} = \min_{s_j = 0}U_j^+(S^{(0)})
+\begin{cases}
+    U_i^+(S) &= \min_{s_j=0}U_j^+(S), s_i=0\\
+     U_i^-(S)&=\max_{s_j=1}U_j^-(S), s_i=1\\
+\end{cases}
 \end{equation}
-or 
+which we can shorten as:
 \begin{equation}
-    U_i-(S^{(0)} = \max_{s_j = 1}U_j^-(S^{(0)})
+r_iU_i(S) = \min_{s_j=s_i}r_jU_j(S)
 \end{equation}
-The set of inequalities required to initiate the transition is associated with the base graph, and we refer to it accordingly as the base inequalities.
-On the other hand, for each transition there are $l$ sets of inequalities describing the stability of subsequent states under the field that initiated the transition.
-We refer to the part of the design inequalities that describes the stability as the relaxation inequalities.\\
-For the general model where the switching fields $u_i^{+, -}(S)$ are independent, we note that the base inequalities are always solvable.
+where $i$ is the hysteron that flips. We refer to the set of inequalities that is required to initiate the transition as the base inequalities.\\
+Let us now define the field $U_i(S^{(0)}$ which initiates the transition as $U*$.
+On top of the base inequalities, an an additional set of linear inequalities is needed to describe the stability of each of the states $S^{(1)}, ..., S^{(l)}$ under $U*$.
+For the final state $S^{(l)}$, all hysterons must be stable, so that:
+\begin{equation}
+r_jU_j(S^{(l)}) > r_jU* \forall j
+\end{equation}
+For the intermediate states $S^{(1)}, ..., S^{(l-1)}$, all hysterons are stable except for a single hysteron $k$, for which the inequality flips:
+\begin{equation}
+\begin{split}
+r_jU_j(S^{(1)}) &> r_jU* \forall j, j \neq k\\
+r_kU_k(S^{(1)}) &\leq r_kU*\\
+\end{split}
+\end{equation}
+For the general model where the switching fields $U_i^{+, -}(S)$ are independent, we note that the base inequalities are always solvable.
 This is because there is no overlap between the sets of inequalities for the individual transitions, since they describe relations between switching fields at the same state $S^{(0)}$.

### 2022-06-02 Paper_draft.tex
Reworked reference to design ineqs to reflect moving section to SI & merged motivation to candidate graphs with corresponding method section; changed title of model section

@@
 Finally, we illustrate our formalism for a model where hysterons are linearly coupled.\\
-\section{Setup}
+\section{Model}
 Here we detail the basic setup for simulating a system of $N$ hysterons. We define the state of the system $S$ as
@@
 
-\section{Topological approach}
+\section{Constructing possible graphs}
 In past work from our group, the possible transition graphs for two- and three-hysteron systems were found using numerical sampling.
@@
 We first construct a number of candidate graphs, which describe the behaviour of a hysteron system in a well-defined way but are not necessarily realizable.
-We then generate a set of inequalities that the switching fields must obey so that the given candidate graph is obtained.
-Finally, we check whether the candidate graph can be realized by checking whether the generated set of inequalities has a solution.
-We thus obtain a list of possible graphs.\\
+We then check whether each graph is realizable by evaluating whether there is a region in the parameter space of switching fields corresponding to the graph.\\
+The region in parameter space associated with each graph is bounded by a set of linear inequalities that the switching fields must obey, which we refer to as the design inequalities.
+We generate the design inequalities systematically by combining the conditions on each individual transition (see SI).
+If the solution space of a graph's design inequalities is not empty, then the graph is realizable.
+Thus, one can find the possible graphs for $N$ hysterons by first generating the candidate graphs, then checking whether each graph's design inequalities have a solution.\\
 In addition to being an efficient method for conclusively finding the possible graphs, the method of candidate graphs also allows us to consider rational design of graphs.
 We can use the candidate graph method to directly consider the possibility of the interesting behaviours that have been observed previously, such as multiperiodic cycles and long transients, for a  given number of hysterons.\\
-\section{Constructing graphs}\label{sec:constructing_graphs}
-We here establish a method for finding the transition graphs that are possible for coupled hysterons.
+We here establish our method for finding the transition graphs that are possible for coupled hysterons.
 We first discuss in section \ref{ssec:candidate_graphs} how one can generate a list of candidate graphs that includes all possible graphs for a given number of hysterons $N$.

### 2022-06-02 Paper_draft.tex
Changed instance of 'all-zero/all-one states' to 'saturated states'

@@
 \subsection{Candidate graphs}\label{ssec:candidate_graphs}
-A well-defined transition graph for $N$ hysterons consists out of $2^N$ states, and $2(2^N-1)$ transitions, namely the up transitions for each state except the all-ones state and the down transitions for each state except the all-zero state.
+A well-defined transition graph for $N$ hysterons consists out of $2^N$ states, and $2(2^N-1)$ transitions, namely the up and down transitions from each state, except for the saturated states which only have one transition each.
 A transition graph is constructed by choosing a transition path for each of these $2(2^N-1)$ transitions.

### 2022-06-03 Paper_draft.tex
Minor change: 'in previous work from our group' replaced by 'in recent work
Reworked section on avalanches by expanding on how to construct l=2 avalanches & added corresponding figure

@@
 \section{Constructing possible graphs}
-In past work from our group, the possible transition graphs for two- and three-hysteron systems were found using numerical sampling.
+In recent work, the transition graphs for two- and three-hysteron systems were found using numerical sampling.
 The obtained graphs contain several noteworthy phenomena that are not possible in the Preisach model, such as breaking of loop return point memory, scrambling, multiperiodic cycles and long transients (Van Hecke, 2021).\\
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{constructing_avalanches_sketch.png}
-    \caption{Construction of an example $N=2$ graph by iteratively building up the avalanche $11\downarrow 10\downarrow 00$.}
+    \includegraphics[width=0.5\textwidth]{constructing_avalanches_sketch_2.png}
+    \caption{Construction of an $l=2$ avalanche by combining an incoming transition with one of at most two outgoing transitions.
+a) Combination of an incoming up transition with an outgoing up transition (ferromagnetic) or down transition (antiferromagnetic).
+b) Combination of an incoming down transition with an outgoing up transition (antiferromagnetic) or down transition (ferromagnetic) }
     \label{fig:avalanches}
 \end{figure}
-We here show how the possible avalanches are evaluated for a given base graph.\\
-We first note that we can build up avalanches iteratively.
-Namely, to have the $l=3$ avalanche $S^{(0)}\rightarrow S^{(1)} \rightarrow S^{(2)}$, one must at least have the $l=2$ avalanche $S^{(0)}\rightarrow S^{(1)}$.
-Thus, we start by evaluating all $l=2$ avalanches.\\
-To have a possible avalanche $S^{(0)}\rightarrow S^{(1)} \rightarrow S^{(2)}$, there must be an incoming transition $S^{(0)}\rightarrow S^{(1)}$ at the state $S^{(1)}$, as well as an outcoming transition $S^{(1)} \rightarrow S^{(2)}$.
-Therefore, we can systematically find all possible $l=2$ avalanches in a base graph by constructing all combinations of incoming and outgoing transitions at each state.
-In addition, it must be checked for each avalanche that $S^{(0)} \neq S^{(2)}$, as an avalanche cannot revisit the same state.\\
-Next, we consider how the avalanche length $l$ can be iterated over to obtain graphs with longer avalanches.
-In the previous step, we have explored all possible combinations of $l=2$ avalanches for the given base graph.
-To have an $l=3$ avalanche, an $l=2$ avalanche must be extended with an additional transition.
-Thus, similarly to our method for finding the $l=2$ avalanches, we find all $l=3$ avalanches for a given graph with only $l=2$ by evaluating all combinations of incoming $l=2$ and outgoing $l=1$ transitions at each state.\\
-In summary, to construct all possible graphs for $N$ hysterons, we first construct all base graphs.
-We then generate the candidate graphs for each base graph by constructing the possible avalanches, and evaluating each combination of avalanches.\\
+We here show how the possible avalanches are evaluated for a given base graph.We first describe how one systematically constructs the possible avalanches of length $l=2$ for a base graph.
+We then generalize our method to avalanches of any length $l$\\
+Let a base graph contain the up transition $S^{(0)}\uparrow S^{(1)}$.
+The state $S^{(1)}$ has two possible transitions: an up transition $S^{(1)}\uparrow S^{(2+)}$, and a down transition  $S^{(1)}\downarrow S^{2-}$.
+The transition $S^{(0)}\uparrow S^{(1)}$ can thus be extended to a $l=2$ avalanche in two ways: either by the ferromagnetic avalanche $S^{(0)}\uparrow S^{(1)}\uparrow S^{(2+)}$, or by the antiferromagnetic avalanche $S^{(0)}\uparrow S^{(1)}\downarrow S^{(2-)}$ (Fig.
+\ref{fig:avalanches}a).
+Similarly, a down transition $S^{(0)}\downarrow S^{(1)}$ can be extended to the antiferromagnetic avalanche $S^{(0)}\downarrow S^{(1)}\uparrow S^{(2+)}$, or to the ferromagnetic avalanche  $S^{(0)}\downarrow S^{(1)}\downarrow S^{(2-)}$ (Fig.
+\ref{fig:avalanches}b).
+Therefore, for each transition $S^{(0)}\rightarrow S^{(1)}$, there is one possible ferromagnetic and one antiferromagnetic avalanche when $S^{(1)}$ is not a saturated state.
+In the case where $S^{(1)}$ is saturated, only the antiferromagnetic option exists.\\
+ We see that every transition $S^{(0)}\rightarrow S^{(1)}$ in the base graph can be extended to a $l=2$ transition  $S^{(0)}\rightarrow S^{(1)}\rightarrow S^{(2)}$ in at most two ways.
+However, not every avalanche is necessarily valid.
+This is because an avalanche may not contain any cycles: if an avalanche did contain a cycle, it would lead to an infinite loop.
+We must therefore impose that $S^{(2)} \neq S^{(0)}$.
+As a result, the number of avalanche options per transition is either two, one, or zero.\\
+
 \section{Application to specific models}

### 2022-06-03 Paper_draft.tex
Added comment on base/relaxation ineqs to piece on avalanches

@@
 In the case where $S^{(1)}$ is saturated, only the antiferromagnetic option exists.\\
- We see that every transition $S^{(0)}\rightarrow S^{(1)}$ in the base graph can be extended to a $l=2$ transition  $S^{(0)}\rightarrow S^{(1)}\rightarrow S^{(2)}$ in at most two ways.
+ We see that every transition $S^{(0)}\rightarrow S^{(1)}$ in the base graph can be extended to a $l=2$ transition  $S^{(0)}\rightarrow S^{(1)}\rightarrow S^{(2)}$ in at most two ways, by choosing either $S^{(2)} = S^{(2+)}$ or $S^{(2)} = S^{(2-)}$ .
 However, not every avalanche is necessarily valid.
@@
 As a result, the number of avalanche options per transition is either two, one, or zero.\\
-
+By extending one of the transitions ina  graph from length $l=1$ to length $l=2$, we modify its design inequalities (see SI).
+In particular, we change the relaxation inequalities that describe the stability of the state $S^{(1)}$.
+We also add a new set of relaxation inequalities so that the state $S^{(2)}$ is stable.\\
 \section{Application to specific models}

### 2022-06-03 Paper_draft.tex
Added comment that term GoE states is customary
Added scrambled graphs to base graphs fig that are possible for general, but not linear coupling

@@
 It often occurs that one or more of the possible states for $N$ hysterons cannot be reached from the ground state.
-We refer to such states which cannot be reached as garden-of-Eden states.
+As is customary, we refer to states that cannot be reached as garden-of-Eden states.
 Because the transitions from garden-of-Eden states are irrelevant when one starts from the ground state, as is generally the case in our experiments, we may choose to ignore garden-of-Eden states.
@@
 b) Preisach graphs for $N=3$.
-c) Scrambled base graphs for N=3 that are possible for linear coupling.}
+c) Scrambled base graphs for N=3 that are possible for linear coupling.
+d) Scrambled base graphs that are possible for general, but not linear model.}
     \label{fig:basegraphs_n3}

### 2022-06-09 Paper_draft.tex
Added overview figure for N=2, l=2 graphs
Added in-text reference to overview figure of N=2, l=2 graphs

@@
 \end{figure}
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=0.5\textwidth]{N2l2_overview.png}
+    \caption{All combinations of $l=2$ avalanches for one of the two base graphs for $N=2$ (top-left) graph, with indication of graphs that of which the design inequalities are solvable (green), solvable except for the final set of relaxation inequalities (orange) and unsolvable (red).}
+    \label{fig:N2l2}
+\end{figure}
 We here show how the possible avalanches are evaluated for a given base graph.We first describe how one systematically constructs the possible avalanches of length $l=2$ for a base graph.
@@
  We see that every transition $S^{(0)}\rightarrow S^{(1)}$ in the base graph can be extended to a $l=2$ transition  $S^{(0)}\rightarrow S^{(1)}\rightarrow S^{(2)}$ in at most two ways, by choosing either $S^{(2)} = S^{(2+)}$ or $S^{(2)} = S^{(2-)}$ .
-However, not every avalanche is necessarily valid.
-This is because an avalanche may not contain any cycles: if an avalanche did contain a cycle, it would lead to an infinite loop.
-We must therefore impose that $S^{(2)} \neq S^{(0)}$.
-As a result, the number of avalanche options per transition is either two, one, or zero.\\
-By extending one of the transitions ina  graph from length $l=1$ to length $l=2$, we modify its design inequalities (see SI).
-In particular, we change the relaxation inequalities that describe the stability of the state $S^{(1)}$.
-We also add a new set of relaxation inequalities so that the state $S^{(2)}$ is stable.\\
+We must check for each of these transitions that $S^{(2)} \neq S^{(0)}$, because an avalanche cannot contain any cycles.
+By then evaluating all combinations of valid avalanches, we obtain a list of candidate graphs for each base graph.
+An example for one of the $N=2$ base graphs is shown in Fig.
+\ref{fig:N2l2}.
+For the example shown, the base graph has four possible $l=2$ avalanches all associated with a different transition ($00\uparrow 01\uparrow 11$, $01\uparrow11\downarrow10$, $11\downarrow10\downarrow00$, and $10\downarrow00\uparrow01$), and therefore $2^4=16$ candidate graphs.\\
 \section{Application to specific models}

### 2022-06-09 Paper_draft.tex
Added reasoning for l=3 graphs from l=2 & generalization

@@
 For the example shown, the base graph has four possible $l=2$ avalanches all associated with a different transition ($00\uparrow 01\uparrow 11$, $01\uparrow11\downarrow10$, $11\downarrow10\downarrow00$, and $10\downarrow00\uparrow01$), and therefore $2^4=16$ candidate graphs.\\
+Thus far, we have only considered avalanches of length $l=2$. We now describe how we construct graphs that have avalanches of length $l=3$ based on the graphs that have only $l=2$.\\
+Suppose that we have a graph containing only $l=2$ avalanches.
+Similarly to how we can find $l=2$ avalanches for a base graph by evaluating combinations of incoming and outgoing transitions from the state $S^{(1)}$, we can construct possible $l=3$ avalanches by finding all combinations of $l=2$ avalanches and outgoing $l=1$ transitions for the given graph.
+From the possible $l=3$ avalanches, we can again construct a list of candidate graphs.\\
+We now ask which $l=2$ graphs should be used as our new 'base' for the $l=3$ graphs.
+It is insufficient to use only the $l=2$ graphs that are themselves realizable, as it is not guaranteed that a derived $l=3$ graph will also be impossible.\\
+We observe that, when extending a $l=2$ avalanche to a $l=3$ avalanche, most of the conditions required for the $l=2$ avalanche are still included in the conditions for the $l=3$ avalanche (see SI).
+The only exception is the final set of relaxation inequalities that describes the stability of the state $S^{(2)}$, which is stable for the $l=2$ transition but unstable for the $l=3$ transition.
+As a result, we can predict that for a $l=2$ graph of which any of the first $l-1$ relaxation inequalities are incompatible, any derived graphs with longer avalanches must also be impossible.\\
+We can thus distinguish three groups of $l=2$ graphs, as indicated in Fig.
+\ref{fig:N2l2}.
+The first group of graphs is realizable, and can therefore also be used as a base to construct $l=3$ graphs.
+For the second group, the graphs themselves are not realizable, but derived $l=3$ graphs may be realizable.
+For the third group, neither the $l=2$ graphs themselves nor any derived graphs containing longer avalanches are realizable.
+To construct all possible $l=3$ graphs, we only need to use graphs from the first two groups.\\
+We now generalize our method.
+To find all graphs with avalanches of length $l$, we construct the graphs for $l-1$, and divide the graphs into the three groups as described.
+We then construct all possible $l=l$ candidate graphs for each of the $l=l-1$ graphs in the first two groups.
+We can thus iterate over $l$ to find all possible graphs.
+Our algorithm terminates when none of the graphs belonging to the first and second groups have any possible avalanches of length $l$.
+
 \section{Application to specific models}

### 2022-06-09 Paper_draft.tex

@@
 We here show how the possible avalanches are evaluated for a given base graph.We first describe how one systematically constructs the possible avalanches of length $l=2$ for a base graph.
-We then generalize our method to avalanches of any length $l$\\
+We then generalize our method to find graphs containing avalanches of any length $l$.\\
+To help our notation, we define $L$ as the length of the longest avalanche in a graph.
+For example, $L=2$ denotes a graph that contains at least one avalanche of length $l=2$, and no $l=3$ avalanches.
+In particular, $L=1$ denotes a base graph.\\
 Let a base graph contain the up transition $S^{(0)}\uparrow S^{(1)}$.
@@
 For the example shown, the base graph has four possible $l=2$ avalanches all associated with a different transition ($00\uparrow 01\uparrow 11$, $01\uparrow11\downarrow10$, $11\downarrow10\downarrow00$, and $10\downarrow00\uparrow01$), and therefore $2^4=16$ candidate graphs.\\
-Thus far, we have only considered avalanches of length $l=2$. We now describe how we construct graphs that have avalanches of length $l=3$ based on the graphs that have only $l=2$.\\
-Suppose that we have a graph containing only $l=2$ avalanches.
-Similarly to how we can find $l=2$ avalanches for a base graph by evaluating combinations of incoming and outgoing transitions from the state $S^{(1)}$, we can construct possible $l=3$ avalanches by finding all combinations of $l=2$ avalanches and outgoing $l=1$ transitions for the given graph.
+Thus far, we have only considered $L=2$ graphs. We now describe how we construct graphs that have avalanches of length $L=3$ based on the $L=2$ graphs.\\
+Suppose that we have a $L=2$ graph.
+Similarly to how we can find $l=2$ avalanches for a base graphs by evaluating combinations of incoming and outgoing transitions, we can construct possible $l=3$ avalanches by finding all combinations of $l=2$ avalanches and outgoing $l=1$ transitions for the given graph.
 From the possible $l=3$ avalanches, we can again construct a list of candidate graphs.\\
-We now ask which $l=2$ graphs should be used as our new 'base' for the $l=3$ graphs.
-It is insufficient to use only the $l=2$ graphs that are themselves realizable, as it is not guaranteed that a derived $l=3$ graph will also be impossible.\\
+We now ask which $L=2$ graphs should be used as our new 'base' for the $L=3$ graphs.
+It is insufficient to use only the $L=2$ graphs that are themselves realizable, as it is not guaranteed that a derived $l=3$ graph will also be impossible.\\
 We observe that, when extending a $l=2$ avalanche to a $l=3$ avalanche, most of the conditions required for the $l=2$ avalanche are still included in the conditions for the $l=3$ avalanche (see SI).
 The only exception is the final set of relaxation inequalities that describes the stability of the state $S^{(2)}$, which is stable for the $l=2$ transition but unstable for the $l=3$ transition.
-As a result, we can predict that for a $l=2$ graph of which any of the first $l-1$ relaxation inequalities are incompatible, any derived graphs with longer avalanches must also be impossible.\\
+As a result, we can predict that for a $L=2$ graph of which the base inequalities and the first set of relaxation inequalities are incompatible, any derived graphs with longer avalanches must also be impossible.\\
 We can thus distinguish three groups of $l=2$ graphs, as indicated in Fig.
@@
 We now generalize our method.
-To find all graphs with avalanches of length $l$, we construct the graphs for $l-1$, and divide the graphs into the three groups as described.
-We then construct all possible $l=l$ candidate graphs for each of the $l=l-1$ graphs in the first two groups.
-We can thus iterate over $l$ to find all possible graphs.
+To find all  $L=l$ graphs, we construct the graphs for $L=l-1$, and divide the graphs into the three groups as described.
+We then construct all $L=l$ candidate graphs for each of the $l=l-1$ graphs in the first two groups.
+We can thus iterate over $L$ to find all possible graphs.
 Our algorithm terminates when none of the graphs belonging to the first and second groups have any possible avalanches of length $l$.

### 2022-06-10 Paper_draft.tex
Added reference to base graphs figure in piece about base graphs
Reworked figure for base graphs for better readability & organisation by main loop

@@
 Because the number of graphs for which the design inequalities need to be explicitly generated is then reduced, the base graph method has an improved efficiency compared to the naive approach.
+\\
 \begin{figure}
@@
 \end{figure}
-\begin{figure}
+\begin{figure*}[ht!]
     \centering
-    \includegraphics[width=0.5\textwidth]{base_graphs.png}
+    \includegraphics[width=0.8\textwidth]{base_graphs.png}
     \caption{All possible base graphs for the two- and three-hysteron systems.
 a) All base graphs for $N=2$; since scrambling is not possible for $N=2$, the base graphs are the two Preisach graphs.
-b) Preisach graphs for $N=3$.
-c) Scrambled base graphs for N=3 that are possible for linear coupling.
-d) Scrambled base graphs that are possible for general, but not linear model.}
+b) All Preisach (top) and scrambled (bottom) base graphs for $N=3$.
+Graphs on a gray background are possible for general, but not linear coupling.}
     \label{fig:basegraphs_n3}
-\end{figure}
+\end{figure*}
 In addition to the base graph method being an efficient method for generating candidate graphs, it also providedes us with a powerful framework for understanding the effects of hysteron interactions on the allowed transition graphs.
@@
 In the Preisach model, the ordering of the main loop fixes the transitions throughout the transition graph, so that each main loop corresponds to a unique Preisach graph.
-Because the down boundary of the main loop has $N!$ permutations, there are $N!$ Preisach graphs for a system of $N$ hysterons.\\
+Because the down boundary of the main loop has $N!$ permutations, there are $N!$ Preisach graphs for a system of $N$ hysterons (Fig.\ref{fig:basegraphs_n3}a-b).\\
 In a scrambled graph, one or more of the transitions in the graph deviates from the main loop.

### 2022-06-13 Paper_draft.tex

@@
 \subsubsection{Base graphs}
-An advantage of the concept of base graphs is that, in the absence of avalanches, it is still relatively straightforward to count the number of possible graphs.
-We will now show how the number of base graphs increases in the presence of scrambling.\\
-Scrambling entails that the ordering of switching fields can change throughout the graph.
+We here show how we generate the list of base graphs for $N$ hysterons, which is subsequently used to construct the full list of candidate graphs.
+We first explain how base graphs can be divided up into Preisach and scrambled graphs.
+We then detail how one can count the number of base graphs per main loop.\\
+We can distinguish between two groups of base graphs.
+First, there are the Preisach graphs, which are possible without coupling.
+Second, there is a group of scrambled graphs, which are possible for interacting hysterons.
+Scrambling is a phenomenon previously seen in interacting hysterons (Van Hecke, 2021; Bense, 2021), where the order in which hysterons flip is not the same throughout the graph.
+It occurs when the ordering between the switching fields of two hysterons in the same phase are changed by one or more hysterons, and is therefore only possible for three or more hysterons.
+Remarkably, having introduced the concept of base graphs, we can identify scrambling as a feature of the base graph.
+We can thus separate the two coupling effects of scrambling and avalanches.\\
 In order to discuss scrambling more explicitly, we here define the main loop as the series of up and down transitions connecting the two saturated states.
 In the Preisach model, the ordering of the main loop fixes the transitions throughout the transition graph, so that each main loop corresponds to a unique Preisach graph.
-Because the down boundary of the main loop has $N!$ permutations, there are $N!$ Preisach graphs for a system of $N$ hysterons (Fig.\ref{fig:basegraphs_n3}a-b).\\
-In a scrambled graph, one or more of the transitions in the graph deviates from the main loop.
-Therefore, when scrambling is allowed, there are multiple possible graphs for each main loop.
-We will now explicitly calculate the number of base graphs per main loop.\\
-To start with, we observe that the number of possible up and down flips for a state $S$ depends on the number of hysterons that is in phase 0 or 1. Defining the magnetisation of a state as
+The number of main loops is the number of permuatations times the number of permutations of the down boundary, which is $N!^2$.
+However, we fix the up boundary when accounting for exchange symmetry, thus dividing the number of main loops by $N!$.
+Therefore, when accounting for exchange symmetry, there are only $N!$ main loops and therefore $N!$ Preisach graphs.
+In a scrambled graph, one or more of the transitions in the graph deviates from the main loop, so that each main loop corresponds to a number of base graphs (Fig.\ref{fig:basegraphs_n3}).\\
+We now explicitly calculate the number of base graphs per main loop.
+To start with, we observe that the number of possible up and down flips for a state $S$ depends on the number of hysterons that is in phase 0 or 1.
+Defining the magnetisation of a state as
 \begin{equation}
@@
 \end{equation}
-we can state that the number of possible up flips for a state $S$ is equal to $N-M(S)$, while the number of possible down flips is $M(S)$.
-To calculate the number of possible graphs, it makes sense to iterate over the magnetisation.\\
+we can state that the number of possible up flips for a state $S$ is equal to $N-M(S)$, while the number of possible down flips is $M(S)$.\\
 Next, we ask how many states exist with the magnetisation $M$.
@@
 \end{equation}
-The number of graphs given by Equation \label{eq:graph_count} takes into account exchange symmetry, but not garden-of-Eden states (Section \ref{ssec:candidate_graphs}), and thus gives a maximum on the number of base graphs.
-For example, for $N=3$, the number of base graphs provided by Equation \ref{eq:graph_count} is 96, while ignoring garden-of-Eden states reduces the number of base graphs to 35 (Fig.
+The number of graphs given by Equation \ref{eq:graph_count} takes into account exchange symmetry, but not garden-of-Eden states (Section \ref{ssec:candidate_graphs}).
+When garden-of-Eden states are excluded, the number of base graphs turns out lower than that given in equation \ref{eq:graph_count}.
+For example, for $N=3$, the number of base graphs provided by Equation \ref{eq:graph_count} is 96, while excluding garden-of-Eden states reduces the number of base graphs to 35 (Fig.
 \ref{fig:basegraphs_n3}).

### 2022-06-13 Paper_draft.tex
Added bibliography file and 4 citations

@@
 Recent work has shown that the many metastable states in frustrated systems can lead to unusual pathways when the system is subject to driving.
-For a variety of systems, including sheared amorphous solids (Nagel, 2021; Keim \& Paulsen, 2019), crumpled thin sheets (Lahini, 2021), corrugated sheets (Bense, 2021) and origami structures (Lechenault, 2021) remarkable phenomena such as breaking of return-point memory, a multiperiodic response to cyclical driving, and transient memory as described by the park bench model(Nagel, 2021; Keim \& Paulsen, 2019) have been observed.\\
+For a variety of systems, including sheared amorphous solids\cite{lindeman2021}( Keim \& Paulsen, 2019), crumpled thin sheets (Lahini, 2021), corrugated sheets\cite{bense2021} and origami structures (Lechenault, 2021) remarkable phenomena such as breaking of return-point memory, a multiperiodic response to cyclical driving, and transient memory as described by the park bench model(Nagel, 2021; Keim \& Paulsen, 2019) have been observed.\\
 It turns out that the response of many frustrated systems can be captured by an interacting collection of hysteretic two-state elements, called hysterons.
-The hysteron model, first suggested by Ferenc Preisach (Preisach, 1935), has long been used to model hysteretic systems as a collection of small hysteretic two-state elements.
+The hysteron model, first suggested by Ferenc Preisach\cite{preisach1935}, has long been used to model hysteretic systems as a collection of small hysteretic two-state elements.
 However, the Preisach model considers hysterons to be independent, while the interacting hysteron model has remained largely unexplored.
@@
 Numerical sampling work from our group has shown that the number of possible transition graphs for a system of interacting hysterons increases dramatically with the number of hysterons.
-For as few as three interacting hysterons, over 15,000 distinct graphs are found (Van Hecke, 2021).
+For as few as three interacting hysterons, over 15,000 distinct graphs are found\cite{vhecke2021}.
 Because the number of possible transition graphs quickly grows overwhelming, a systematic method will be needed for categorizing the graphs.\\
@@
 \subsection{Linear coupling}
-%\begin{figure}[!ht]
-%    \centering
-%    \includegraphics[width=0.5\textwidth]{.png}
-%    \caption{Overview of possible scrambling and avalanches in the linear model for a single nonzero $c_ij$.}
-%    \label{fig:linear_coupling}
-%\end{figure}\\
 \subsection{Hysterons in series}
@@
 \section{Outlook}
-%\bibliography{apssamp}% Produces the bibliography via BibTeX.
+
+\bibliography{test}% Produces the bibliography via BibTeX.
 

### 2022-06-13 Paper_draft.tex
Corrected inconsistency in notation of switching fields

@@
 where $s_i \in \{0, 1\}$ are the phases of individual hysterons.
-We then model the response of individual hysterons to an external driving field $U$ by defining up and down switching fields $u_i^+$ and $u_i^-$.
-A hysteron transitions from phase 0 to 1 ('up') if $U \geq u_i^+$, and from phase 1 to 0 ('down') if $U \leq u_i^-$.\\
-If the system of hysterons is non-interacting, then the switching fields $\{u_i^+\}, \{u_i^-\}$ are fixed values $u_i^{+, -}$.
+We then model the response of individual hysterons to an external driving field $U$ by defining up and down switching fields $U_i^+$ and $U_i^-$.
+A hysteron transitions from phase 0 to 1 ('up') if $U \geq U_i^+$, and from phase 1 to 0 ('down') if $U \leq U_i^-$.\\
+If the system of hysterons is non-interacting, then the switching fields $\{U_i^+\}, \{U_i^-\}$ are fixed values $u_i^{+, -}$.
 We refer to these switching fields in the absence of interactions as the bare switching fields.

### 2022-06-14 Paper_draft.tex
Added remaining references

@@
 \usepackage{amsmath}
-%\usepackage{hyperref}% add hypertext capabilities
+\usepackage{hyperref}% add hypertext capabilities
 %\usepackage[mathlines]{lineno}% Enable numbering of text and display math
@@
 Recent work has shown that the many metastable states in frustrated systems can lead to unusual pathways when the system is subject to driving.
-For a variety of systems, including sheared amorphous solids\cite{lindeman2021}( Keim \& Paulsen, 2019), crumpled thin sheets (Lahini, 2021), corrugated sheets\cite{bense2021} and origami structures (Lechenault, 2021) remarkable phenomena such as breaking of return-point memory, a multiperiodic response to cyclical driving, and transient memory as described by the park bench model(Nagel, 2021; Keim \& Paulsen, 2019) have been observed.\\
+For a variety of systems, including sheared amorphous solids\cite{lindeman2021}\cite{keimpaulsen2021}, crumpled thin sheets\cite{shohat2021}, corrugated sheets\cite{bense2021} and origami structures\cite{juleslechenault2021} remarkable phenomena such as breaking of return-point memory, a multiperiodic response to cyclical driving, and transient memory as described by the park bench model \cite{lindeman2021}\cite{keimpaulsen2019} have been observed.\\
 It turns out that the response of many frustrated systems can be captured by an interacting collection of hysteretic two-state elements, called hysterons.
@@
 The recent experimental findings show that the interacting hysteron model is relevant for many physical systems, and thus worth examining in more detail.\\
-The possible metastable states and transitions between these states for a given hysteron system can be portrayed as a directed graph, which captures all possible responses of the system to driving (Regev, 2019).
+The possible metastable states and transitions between these states for a given hysteron system can be portrayed as a directed graph, which captures all possible responses of the system to driving\cite{regev2019}.
 Numerical sampling work from our group has shown that the number of possible transition graphs for a system of interacting hysterons increases dramatically with the number of hysterons.
@@
 In recent work, the transition graphs for two- and three-hysteron systems were found using numerical sampling.
-The obtained graphs contain several noteworthy phenomena that are not possible in the Preisach model, such as breaking of loop return point memory, scrambling, multiperiodic cycles and long transients (Van Hecke, 2021).\\
+The obtained graphs contain several noteworthy phenomena that are not possible in the Preisach model, such as breaking of loop return point memory, scrambling, multiperiodic cycles and long transients\cite{vhecke2021}.\\
 A significant disadvantage of numerical sampling is that it is not conclusive, as it is always possible that a region in parameter space leading to a certain transition graph is missed.
@@
 Second, there is a group of scrambled graphs, which are possible for interacting hysterons.
-Scrambling is a phenomenon previously seen in interacting hysterons (Van Hecke, 2021; Bense, 2021), where the order in which hysterons flip is not the same throughout the graph.
+Scrambling is a phenomenon previously seen in interacting hysterons\cite{vhecke2021}\cite{bense2021}, where the order in which hysterons flip is not the same throughout the graph.
 It occurs when the ordering between the switching fields of two hysterons in the same phase are changed by one or more hysterons, and is therefore only possible for three or more hysterons.
@@
 
-\bibliography{test}% Produces the bibliography via BibTeX.
+\bibliography{mybibliography}% Produces the bibliography via BibTeX.
+\bibliographystyle{apsrev}
 

### 2022-06-14 Paper_draft.tex
Added numbers for permutations of switching fields

@@
 In practice, however, it is impractical to find the possible transition graphs by evaluating all possible orderings.
-This is because the transition graph only depends on a partial order of the switching fields, not on the total order, so that the number of permutations vastly outweighs the number of possible graphs.\\
+This is because the transition graph only depends on a partial order of the switching fields, not on the total order, so that the number of permutations vastly outweighs the number of possible graphs.
+For example, for the interacting two-hysteron system, there are eight switching fields, giving $8!
+= 40320$ permutations, and for $N=3$ the number of permutations is $24!
+\approx 6\times 10^{23}$.\\
 Instead of evaluating all permutations of the total order of the switching fields, we find it more useful to take a reverse approach by starting from the topology.
@@
 As a result, we can predict that for a $L=2$ graph of which the base inequalities and the first set of relaxation inequalities are incompatible, any derived graphs with longer avalanches must also be impossible.\\
-We can thus distinguish three groups of $l=2$ graphs, as indicated in Fig.
+We can thus distinguish three groups of $L=2$ graphs, as indicated in Fig.
 \ref{fig:N2l2}.
-The first group of graphs is realizable, and can therefore also be used as a base to construct $l=3$ graphs.
-For the second group, the graphs themselves are not realizable, but derived $l=3$ graphs may be realizable.
-For the third group, neither the $l=2$ graphs themselves nor any derived graphs containing longer avalanches are realizable.
+The first group of graphs is realizable, and can therefore also be used as a base to construct $L=3$ graphs.
+For the second group, the graphs themselves are not realizable, but derived $L=3$ graphs may be realizable.
+For the third group, neither the $L=2$ graphs themselves nor any derived graphs containing longer avalanches are realizable.
 To construct all possible $l=3$ graphs, we only need to use graphs from the first two groups.\\

### 2022-06-15 Paper_draft.tex
Corrected several instances of l i/o L
Miscellaneous small corrections after going through draft

@@
 We consider this scenario to be ill-defined, as the system's state is caught in an infinite loop.\\
-The system's response to a field $U$ is thus obtained by comparing the field to the switching fields $\{U_i^+\}, \{U_i^-\}$ of the hysterons individually, flipping hysterons that are unstable, and repeating this process until there are no unstable hysterons.
+The system's response to a field $U$ is thus obtained by comparing the field to the switching fields $\{U_i^+\}, \{U_i^-\}$ of the hysterons individually, flipping hysterons that are unstable, and repeating this process until there are no more unstable hysterons.
 The response is ill-defined if multiple hysterons are unstable at the same time, or if the system becomes caught in an infinite self-loop.\\
-The possible responses of a collection of $N$ hysterons to driving are captured by a state transition graph, which consists of all stable states $S$ and all transitions between these states.
+The possible responses of a collection of $N$ hysterons to driving are captured by a state transition graph, which consists of all stable states $S$ and all transitions between states.
 For a system of $N$ hysterons, there are $2^N$ possible states.
@@
 Therefore, a transition graph for a collection of $N$ hysterons consists of a maximum of $2^N$ states and $2(2^N-1)$ transitions.
+It can occur that not all of the $2^N$ states are included in the transition graph, because it is possible for a state to not be reachable, or to only be reachable as an unstable intermediate state of an avalanche.
+We discuss unreachable states in more detail in Section \ref{ssec:candidate_graphs}.
 
@@
 The region in parameter space associated with each graph is bounded by a set of linear inequalities that the switching fields must obey, which we refer to as the design inequalities.
-We generate the design inequalities systematically by combining the conditions on each individual transition (see SI).
+We generate the design inequalities systematically by combining the conditions on each individual transition.
+We describe how the design inequalities are found in the Supplemental Information.
 If the solution space of a graph's design inequalities is not empty, then the graph is realizable.
@@
 It often occurs that one or more of the possible states for $N$ hysterons cannot be reached from the ground state.
-As is customary, we refer to states that cannot be reached as garden-of-Eden states.
-Because the transitions from garden-of-Eden states are irrelevant when one starts from the ground state, as is generally the case in our experiments, we may choose to ignore garden-of-Eden states.
-As a consequence, when two graphs only differ from one another by transitions that occur from garden-of-Eden states, the graphs become duplicates.
-Therefore, when garden-of-Eden states are ignored, the number of distinct graphs can turn out lower than the number of possible combinations of transitions.
-For $N=2$, ignoring garden-of-Eden states  reduces the number of graphs from 1458 to 752.
+As is customary\cite{juleslechenault2021}, we refer to states that cannot be reached as garden-of-Eden (GoE) states.
+We may choose to exclude GoE states in some cases, for instance in an experimental setup where one starts from the ground state.
+As a consequence of excluding GoE states, when two graphs only differ from one another by transitions that occur from GoE states, the graphs become duplicates.
+Therefore, when GoE states are ignored, the number of distinct graphs can turn out lower than the number of possible combinations of transitions.
+For $N=2$, ignoring GoE states  reduces the number of graphs from 1458 to 752.
 \subsection{Realizability}\label{ssec:realizability}
@@
 \\
-The idea of base graphs allows us to improve our method for generating candidate graphs.
+Using base graphs, we can improve upon our method for generating candidate graphs.
 Namely, by first constructing all base graphs, and only then evaluating all possible avalanches for each base graph individually, we exclude the subgraphs of the type shown in Fig.
@@
 In the Preisach model, the ordering of the main loop fixes the transitions throughout the transition graph, so that each main loop corresponds to a unique Preisach graph.
-The number of main loops is the number of permuatations times the number of permutations of the down boundary, which is $N!^2$.
+We additionally define the up and down boundary of the main loop as the series of up (down) transitions going from the state with all $s_i=0$ (1) to that with all $s_i=1$ (0).
+The number of main loops is then the number of permutations of the up boundary times that of the down boundary.
+Because both the up and down boundary consist of $N$ flips, there are $N!^2$ main loops.
 However, we fix the up boundary when accounting for exchange symmetry, thus dividing the number of main loops by $N!$.
-Therefore, when accounting for exchange symmetry, there are only $N!$ main loops and therefore $N!$ Preisach graphs.
+Therefore, when accounting for exchange symmetry, there are only $N!$ main loops and resulting Preisach graphs.\\
 In a scrambled graph, one or more of the transitions in the graph deviates from the main loop, so that each main loop corresponds to a number of base graphs (Fig.\ref{fig:basegraphs_n3}).\\
@@
 Let a base graph contain the up transition $S^{(0)}\uparrow S^{(1)}$.
-The state $S^{(1)}$ has two possible transitions: an up transition $S^{(1)}\uparrow S^{(2+)}$, and a down transition  $S^{(1)}\downarrow S^{2-}$.
+From the state $S^{(1)}$ there are two possible transitions: an up transition $S^{(1)}\uparrow S^{(2+)}$, and a down transition  $S^{(1)}\downarrow S^{2-}$.
 The transition $S^{(0)}\uparrow S^{(1)}$ can thus be extended to a $l=2$ avalanche in two ways: either by the ferromagnetic avalanche $S^{(0)}\uparrow S^{(1)}\uparrow S^{(2+)}$, or by the antiferromagnetic avalanche $S^{(0)}\uparrow S^{(1)}\downarrow S^{(2-)}$ (Fig.
@@
 Therefore, for each transition $S^{(0)}\rightarrow S^{(1)}$, there is one possible ferromagnetic and one antiferromagnetic avalanche when $S^{(1)}$ is not a saturated state.
-In the case where $S^{(1)}$ is saturated, only the antiferromagnetic option exists.\\
- We see that every transition $S^{(0)}\rightarrow S^{(1)}$ in the base graph can be extended to a $l=2$ transition  $S^{(0)}\rightarrow S^{(1)}\rightarrow S^{(2)}$ in at most two ways, by choosing either $S^{(2)} = S^{(2+)}$ or $S^{(2)} = S^{(2-)}$ .
+In the case where $S^{(1)}$ is saturated, only the antiferromagnetic option exists.
 We must check for each of these transitions that $S^{(2)} \neq S^{(0)}$, because an avalanche cannot contain any cycles.
-By then evaluating all combinations of valid avalanches, we obtain a list of candidate graphs for each base graph.
+We thus obtain a list of avalanches for each base graph, from which we construct a list of candidate graphs by evaluating each combination of avalanches.\\
 An example for one of the $N=2$ base graphs is shown in Fig.
@@
 We now ask which $L=2$ graphs should be used as our new 'base' for the $L=3$ graphs.
-It is insufficient to use only the $L=2$ graphs that are themselves realizable, as it is not guaranteed that a derived $l=3$ graph will also be impossible.\\
+It is insufficient to use only the $L=2$ graphs that are themselves realizable, as it is not guaranteed that a derived $L=3$ graph will also be impossible.\\
 We observe that, when extending a $l=2$ avalanche to a $l=3$ avalanche, most of the conditions required for the $l=2$ avalanche are still included in the conditions for the $l=3$ avalanche (see SI).
 The only exception is the final set of relaxation inequalities that describes the stability of the state $S^{(2)}$, which is stable for the $l=2$ transition but unstable for the $l=3$ transition.
-As a result, we can predict that for a $L=2$ graph of which the base inequalities and the first set of relaxation inequalities are incompatible, any derived graphs with longer avalanches must also be impossible.\\
+As a result, we can predict that for a $L=2$ graph of which the base inequalities and the first set of relaxation inequalities are incompatible, any derived graphs with longer avalanches must also be impossible.
+If, however, it is only the last set of relaxation inequalities that causes the graph to be impossible, then a derived graph of $L=3$ or higher may still be realizable.\\
 We can thus distinguish three groups of $L=2$ graphs, as indicated in Fig.
@@
 For the third group, neither the $L=2$ graphs themselves nor any derived graphs containing longer avalanches are realizable.
-To construct all possible $l=3$ graphs, we only need to use graphs from the first two groups.\\
+To construct all possible $L=3$ graphs, we only need to use graphs from the first two groups.\\
 We now generalize our method.
@@
 We then construct all $L=l$ candidate graphs for each of the $l=l-1$ graphs in the first two groups.
-We can thus iterate over $L$ to find all possible graphs.
+We thus have an algorithm that constructs all realizable graphs by iterating over the maximum avalanche length $L$.
 Our algorithm terminates when none of the graphs belonging to the first and second groups have any possible avalanches of length $l$.

### 2022-06-23 Paper_draft.tex

--- 2022-06-14 Paper_draft.tex
@@
 
-\usepackage{graphicx}% Include figure files
+\usepackage[pdftex]{graphicx}% Include figure files
 \usepackage{dcolumn}% Align table columns on decimal point
 \usepackage{bm}% bold math
-\usepackage{xcolor}
+\usepackage[table]{xcolor}
 \newcommand\note[1]{\textcolor{red}{#1}}
@@
 %]{geometry}
+
+\newcommand\x{0.11\textwidth}
 
@@
 It often occurs that one or more of the possible states for $N$ hysterons cannot be reached from the ground state.
-As is customary, we refer to states that cannot be reached as garden-of-Eden states.
+As is customary\cite{juleslechenault2021}, we refer to states that cannot be reached as garden-of-Eden states.
 Because the transitions from garden-of-Eden states are irrelevant when one starts from the ground state, as is generally the case in our experiments, we may choose to ignore garden-of-Eden states.
@@
 \end{figure*}
+\begin{table*}[]
+\begin{tabular}{|c|c|ccc|c|c|cc|}
+\hline
+\textbf{(1, 2, 3)} & \textbf{(1, 3, 2)} & \textbf{(2, 3, 1)}&&& \textbf{(2, 1, 3)} & \textbf{(3, 1, 2)} & \textbf{(3, 1, 2)}&\\ \hline
+  \includegraphics[width=\x]{21-06-2022_N3graphs_preisach/graph0.pdf}
+&\includegraphics[width=\x]{21-06-2022_N3graphs_preisach/graph3.pdf}              
+&\includegraphics[width=\x]{21-06-2022_N3graphs_preisach/graph2.pdf}&&                            
+&\includegraphics[width=\x]{21-06-2022_N3graphs_preisach/graph1.pdf}                                  
+&\includegraphics[width=\x]{21-06-2022_N3graphs_preisach/graph4.pdf}                                  
+&\includegraphics[width=\x]{21-06-2022_N3graphs_preisach/graph5.pdf}& \\ \hline             
+&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph3.pdf}                  
+&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph11.pdf}&\includegraphics[width=\x]{21-06-2022_N3graphs_base_unsolvable/graph1.pdf}\cellcolor{gray!30}   &   \includegraphics[width=\x]{21-06-2022_N3graphs_base_unsolvable/graph2.pdf}\cellcolor{gray!30}
+&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph5.pdf}                   
+&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph0.pdf}                      
+&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph1.pdf}&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph12.pdf}\\ 
+& \includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph4.pdf}                
+&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph13.pdf}&\includegraphics[width=\x]{21-06-2022_N3graphs_base_unsolvable/graph2.pdf}\cellcolor{gray!30}   & \includegraphics[width=\x]{21-06-2022_N3graphs_base_unsolvable/graph7.pdf}\cellcolor{gray!30}
+&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph9.pdf}                     
+&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph6.pdf}                   
+&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph2.pdf}&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph14.pdf}\\
+&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph8.pdf}                  
+&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph19.pdf}&\includegraphics[width=\x]{21-06-2022_N3graphs_base_unsolvable/graph5.pdf}\cellcolor{gray!30}&\includegraphics[width=\x]{21-06-2022_N3graphs_base_unsolvable/graph6.pdf}\cellcolor{gray!30}
+&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph16.pdf}    
+&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph15.pdf}                         
+&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph7.pdf}&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph17.pdf}\\
+&\includegraphics[width=\x]{21-06-2022_N3graphs_base_unsolvable/graph4.pdf}\cellcolor{gray!30}          
+&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph20.pdf}&&                    
+&\includegraphics[width=\x]{21-06-2022_N3graphs_base_unsolvable/graph0.pdf}\cellcolor{gray!30}                    
+&                    
+&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph10.pdf}&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph18.pdf}\\ \hline
+
+\end{tabular}
+\end{table*}
 In addition to the base graph method being an efficient method for generating candidate graphs, it also providedes us with a powerful framework for understanding the effects of hysteron interactions on the allowed transition graphs.

### 2022-06-24 Paper_draft.tex
Finished reworking base graphs figure into Latex table & replaced figure

@@
 \usepackage{amsmath}
+\usepackage{subfig}
 \usepackage{hyperref}% add hypertext capabilities
@@
 \newcommand\x{0.11\textwidth}
+\newcommand\y{0.5\textwidth}
 
@@
 \end{figure}
-\begin{figure*}[ht!]
+\begin{table*}[]
+\begin{minipage}{0.6\textwidth}
+\textbf{a)}\\
 \centering
-    \includegraphics[width=0.8\textwidth]{base_graphs.png}
-    \caption{All possible base graphs for the two- and three-hysteron systems.
-a) All base graphs for $N=2$; since scrambling is not possible for $N=2$, the base graphs are the two Preisach graphs.
-b) All Preisach (top) and scrambled (bottom) base graphs for $N=3$.
-Graphs on a gray background are possible for general, but not linear coupling.}
-    \label{fig:basegraphs_n3}
-\end{figure*}
-\begin{table*}[]
+\begin{tabular}{|c|c|}
+\hline
+\textbf{(1, 2)}&\textbf{(2, 1)}\\ \hline
+  \includegraphics[width=\y]{24-06-2022_N2graphs_preisach/graph0.pdf}
+& \includegraphics[width=\y]{24-06-2022_N2graphs_preisach/graph1.pdf} \\ \hline
+\end{tabular}
+\end{minipage}
+\begin{minipage}{0.95\textwidth}
+\textbf{b)}\\
+\centering
 \begin{tabular}{|c|c|ccc|c|c|cc|}
@@
 &\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph10.pdf}&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph18.pdf}\\ \hline
-
 \end{tabular}
+\end{minipage}
+\caption{All possible base graphs for the two- and three-hysteron systems, indexed per main loop.
+a) All base graphs for $N=2$; since scrambling is not possible for $N=2$, the base graphs are the two Preisach graphs.
+b) All Preisach (top) and scrambled (bottom) base graphs for $N=3$.
+Graphs on a gray background are possible for general, but not linear coupling.}
+\label{fig:basegraphs_n3}
 \end{table*}
@@
 Therefore, when accounting for exchange symmetry, there are only $N!$ main loops and resulting Preisach graphs.\\
-In a scrambled graph, one or more of the transitions in the graph deviates from the main loop, so that each main loop corresponds to a number of base graphs (Fig.\ref{fig:basegraphs_n3}).\\
+In a scrambled graph, one or more of the transitions in the graph deviates from the main loop, so that each main loop corresponds to a number of base graphs (Table.\ref{fig:basegraphs_n3}).\\
 We now explicitly calculate the number of base graphs per main loop.

### 2022-06-24 Paper_draft.tex
Reworked base graph method overview using Tikz

@@
 \usepackage{amsmath}
-\usepackage{subfig}
+\usepackage{tikz}
+\usetikzlibrary{positioning}
+\usetikzlibrary{decorations.pathreplacing,calligraphy}
 \usepackage{hyperref}% add hypertext capabilities
@@
 \subsection{The base graph method}
-\begin{figure}[!ht]
+\begin{figure}[ht!]
 \centering
-    \includegraphics[width=0.5\textwidth]{breakdown_sketch.png}
+\begin{tikzpicture}[squarednode/.style={rectangle, draw=black, fill=white, thick, minimum size=3mm}]
+\node[squarednode](mainloop){Main loop};
+\node[squarednode](scrambling)[right=of mainloop] {Scrambling};
+\node[squarednode](avalanches)[right=of scrambling] {Avalanches};
+\node[squarednode](finalgraph)[right=of avalanches] {Final graph};
+
+\draw[->, very thick] (mainloop.east) -- (scrambling.west);
+\draw[->, very thick] (scrambling.east) -- (avalanches.west);
+\draw[->, very thick] (avalanches.north) arc (-80:260:10pt)
+node[pos=0.5, above=2pt]{Iterate over $l$};
+\draw[decorate, decoration = {calligraphic brace, amplitude=6pt,raise=10pt}, very thick] (mainloop.west)  -- (scrambling.east)
+node[pos=0.5,above=15pt,black] {Base graph};
+\draw[decorate, decoration = {calligraphic brace, amplitude=6pt,raise=10pt}, very thick] (avalanches.east)  -- (scrambling.west)
+node[pos=0.5, below=15pt,black] {Only with coupling}; 
+\draw[->, very thick] (avalanches.east) -- (finalgraph.west);
+\end{tikzpicture}
     \caption{Breakdown of an example transition graph into a base graph and a combination of avalanches.

### 2022-06-28 Paper_draft.tex
Added piece about ordering of switching fields

@@
 We discuss unreachable states in more detail in Section \ref{ssec:candidate_graphs}.
-
+\subsection{Evaluation of switching fields}
+We now describe how the transition graph is constructed for a given set of bare switching fields $\{u_i^{+, -}\}$ and coupling coefficients $c_{ij}$.\\
+We observe that in essence, it is only the ordering of the switching fields ${U_i^{+, -}(S)}$ that determines the state transition graph, rather than their absolute value.
+As a result, there can only be as many graphs as there are permutations of the order of switching fields.
+In the case where hysterons are non-interacting, there are only $2N$ switching fields $\{u_i^{+, -}\}$.
+In addition, because we never compare an up switching field with a down switching fields, the only orderings that can change the graph are the partial orderings of the up switching fields $\{u_i^+\}$ and of the down switching fields $\{u_i^-\}$.
+The number of orderings that can lead to a unique graph is then $N!\times N!$.
+When we fix the up switching fields to account for exchange symmetry, we find that the number of permutations is only $N!$.
+Indeed, we have that there are $N!$ Preisach graphs for a collection of $N$ hysterons, each corresponding to a different main loop.\\
+When hysterons are allowed to interact, however, the situation changes.
+On one hand, there are then $2(2^N-1)$ states $U_i^{+, -}(S)$, and because of the possibility of avalanches, the ordering between all of the states must be considered.
+On the other hand, the state transition graph is only determined by a partial order between some of the switching fields.
+As a result, the number of permutations greatly outnumbers the number of unique state transition graphs.
+For $N=2$, the number of permutations is $8!
+= 40320$ while we know the number of graphs to be 13.
+For $N=3$, the number of permutations is as high as $24!
+\approx 6\times 10^{23}$.\\
+We conclude that it is inefficient to find all graphs for an interacting system of hysterons by considering the permutations of all switching fields.
+Even so, we can make use of the fact that the state transition graph only depends on a partial ordering of the switching fields.
+Namely, we know that each graph has an underlying set of linear inequalities $U_i(S_A) > U_j(S_B)$, which we refer to as the design inequalities\cite{vhecke2021}.
+The solution space of the design inequalities provides the region in parameter space that leads to the given graph.
+In particular, if the design inequalities have no solution, then the given graph is not realizable.\\
 \section{Constructing possible graphs}

### 2022-06-28 Paper_draft.tex
Expanded part on main loops within piece on hysteron ordering

@@
 The number of orderings that can lead to a unique graph is then $N!\times N!$.
-When we fix the up switching fields to account for exchange symmetry, we find that the number of permutations is only $N!$.
-Indeed, we have that there are $N!$ Preisach graphs for a collection of $N$ hysterons, each corresponding to a different main loop.\\
+When we fix the up switching fields to account for exchange symmetry, we find that the number of permutations is only $N!$.\\
+Indeed there are $N!$ Preisach graphs for a collection of $N$ hysterons, each corresponding to a different ordering of the down switching fields.
+The ordering for each graph can be easily identified by considering the main loop: that is, the sequence of down transitions connecting the state with all $s_i = 1$ to that with all $s_i=0$.
+We accordingly use the main loop as an identifier for the Preisach graphs.
+For instance, for $N=2$ there are two Preisach graphs, corresponding to the main loops (1, 2) and (2, 1).\\
+We have shown that it is straightforward to construct all Preisach graphs by considering all permutations of the down switching fields.
 When hysterons are allowed to interact, however, the situation changes.
@@
 On the other hand, the state transition graph is only determined by a partial order between some of the switching fields.
-As a result, the number of permutations greatly outnumbers the number of unique state transition graphs.
+As a result, the number of permutations $(2(2^N-1))!$  for interacting hysterons greatly outnumbers the number of unique state transition graphs.
 For $N=2$, the number of permutations is $8!
-= 40320$ while we know the number of graphs to be 13.
+= 40320$ while we know the number of graphs to be only 13.
 For $N=3$, the number of permutations is as high as $24!
 \approx 6\times 10^{23}$.\\
-We conclude that it is inefficient to find all graphs for an interacting system of hysterons by considering the permutations of all switching fields.
+We thus see that it is inefficient to find all graphs for an interacting system of hysterons by considering the permutations of all switching fields.
 Even so, we can make use of the fact that the state transition graph only depends on a partial ordering of the switching fields.

### 2022-06-28 Paper_draft.tex
Moved pieces about exchange symmetry & Garden of Eden states to model section

@@
 It can occur that not all of the $2^N$ states are included in the transition graph, because it is possible for a state to not be reachable, or to only be reachable as an unstable intermediate state of an avalanche.
-We discuss unreachable states in more detail in Section \ref{ssec:candidate_graphs}.
-\subsection{Evaluation of switching fields}
+We now make two considerations that affect the number of distinct graphs, namely exchange symmetry and Garden-of-Eden states.
+\subsection{Uniqueness considerations}
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.5\textwidth]{exchange_plus_goe.png}
+    \caption{Considerations for removing duplicate graphs: a) exchange symmetry and b) garden-of-Eden states.}
+    \label{fig:exchangeplusgoe}
+\end{figure}
+We now describe two considerations that decrease the number of unique transition graphs, namely the 
+\subsubsection{Exchange symmetry}
+The hysterons in our model are considered as indistinguishable particles.
+That is, when we define the state $S = \{s_1, s_2, ..., s_N\}$, the labelling of hysterons 1 through N is arbitrary.
+As a result, when two graphs only differ from one another by the ordering of the hysterons 1, 2, ..., N, we consider the graphs to be the same (Fig.
+\ref{fig:exchangeplusgoe}a).\\
+To account for exchange symmetry, we fix the order in which hysterons 1, 2, ..., N flip up when increasing the external field from the ground state.
+For example, for $N=3$, we have that hysteron 3 flips up first from the state 000, hysteron 2 flips up first from 001, and trivially hysteron 1 flips up first from 011.
+Since there are $N!$ permutations of the order of $N$ up switching fields, accounting for exchange symmetry decreases the number of candidate graphs by a factor $N!$.
+Thus, for $N=2$, the number of candidate graphs is reduced by a factor 2 from 2916 to 1458.
+\subsubsection{Garden-of-Eden states}
+It often occurs that one or more of the possible states for $N$ hysterons cannot be reached from the ground state.
+As is customary\cite{juleslechenault2021}, we refer to states that cannot be reached as garden-of-Eden (GoE) states.
+We may choose to exclude GoE states in some cases, for instance in an experimental setup where one starts from the ground state.
+As a consequence of excluding GoE states, when two graphs only differ from one another by transitions that occur from GoE states, the graphs become duplicates.
+Therefore, when GoE states are ignored, the number of distinct graphs can turn out lower than the number of possible combinations of transitions.
+For $N=2$, ignoring GoE states  reduces the number of graphs from 1458 to 752.
+\subsection{Ordering of switching fields}
 We now describe how the transition graph is constructed for a given set of bare switching fields $\{u_i^{+, -}\}$ and coupling coefficients $c_{ij}$.\\
@@
 In addition to being an efficient method for conclusively finding the possible graphs, the method of candidate graphs also allows us to consider rational design of graphs.
-We can use the candidate graph method to directly consider the possibility of the interesting behaviours that have been observed previously, such as multiperiodic cycles and long transients, for a  given number of hysterons.\\
+We can use the candidate graph method to directly consider the possibility of the interesting behaviours that have been observed previously, such as multiperiodic cycles and long transients, for a  given number of hysterons.\
 We here establish our method for finding the transition graphs that are possible for coupled hysterons.
@@
 Naively, one can construct all possible transition graphs by finding the possible transition paths for each individual transition.
-For example, for $N=2$ one finds $3^4\times 6^2 = 2916$ graphs (Fig.\ref{fig:transition_paths_N2}).
-We will now make two considerations that reduce the number of candidate graphs, namely exchange symmetry and garden-of-Eden states.
+For example, for $N=2$ one finds $3^4\times 6^2 = 2916$ graphs (Fig.\ref{fig:transition_paths_N2}).\\
 \begin{figure}[ht!]
@@
 \end{figure}
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=0.5\textwidth]{exchange_plus_goe.png}
-    \caption{Considerations for removing duplicate graphs: a) exchange symmetry and b) garden-of-Eden states.}
-    \label{fig:exchangeplusgoe}
-\end{figure}
-\subsubsection{Exchange symmetry}
-The hysterons in our model are considered as indistinguishable particles.
-That is, when we define the state $S = \{s_1, s_2, ..., s_N\}$, the labelling of hysterons 1 through N is arbitrary.
-As a result, when two graphs only differ from one another by the ordering of the hysterons 1, 2, ..., N, we consider the graphs to be the same (Fig.
-\ref{fig:exchangeplusgoe}a).\\
-To account for exchange symmetry, we fix the order in which hysterons 1, 2, ..., N flip up when increasing the external field from the ground state.
-For example, for $N=3$, we have that hysteron 3 flips up first from the state 000, hysteron 2 flips up first from 001, and trivially hysteron 1 flips up first from 011.
-Since there are $N!$ permutations of the order of $N$ hysterons, accounting for exchange symmetry decreases the number of candidate graphs by a factor $N!$.
-Thus, for $N=2$, the number of candidate graphs is reduced by a factor 2 from 2916 to 1458.
-\subsubsection{Garden-of-Eden states}
-It often occurs that one or more of the possible states for $N$ hysterons cannot be reached from the ground state.
-As is customary\cite{juleslechenault2021}, we refer to states that cannot be reached as garden-of-Eden (GoE) states.
-We may choose to exclude GoE states in some cases, for instance in an experimental setup where one starts from the ground state.
-As a consequence of excluding GoE states, when two graphs only differ from one another by transitions that occur from GoE states, the graphs become duplicates.
-Therefore, when GoE states are ignored, the number of distinct graphs can turn out lower than the number of possible combinations of transitions.
-For $N=2$, ignoring GoE states  reduces the number of graphs from 1458 to 752.
 \subsection{Realizability}\label{ssec:realizability}

### 2022-06-28 Paper_draft.tex
Reworked introduction to candidate graphs section to reflect structure change

@@
 Finally, we illustrate our formalism for a model where hysterons are linearly coupled.\\
-\section{Model}
+\section{Model}\label{sec:model}
 Here we detail the basic setup for simulating a system of $N$ hysterons. We define the state of the system $S$ as
@@
 For $N=2$, ignoring GoE states  reduces the number of graphs from 1458 to 752.
-\subsection{Ordering of switching fields}
+\subsection{Ordering of switching fields}\label{ssec:ordering}
 We now describe how the transition graph is constructed for a given set of bare switching fields $\{u_i^{+, -}\}$ and coupling coefficients $c_{ij}$.\\
@@
 A significant disadvantage of numerical sampling is that it is not conclusive, as it is always possible that a region in parameter space leading to a certain transition graph is missed.
-Here we aim to establish a tool that can conclusively find all possible graphs for a given number of hysterons $N$.\\
-Fortunately, it is not necessary to sample all of parameter space.
-The reason for this is that the transition graph for a given system does not depend on the absolute values of the switching fields $U_i^{+,-}(S)$, but only on the order of the switching fields.
-In principle, one could find all possible transition graphs for a given number of hysterons $N$ by evaluating all permutations of the order of the switching fields.\\
-In practice, however, it is impractical to find the possible transition graphs by evaluating all possible orderings.
-This is because the transition graph only depends on a partial order of the switching fields, not on the total order, so that the number of permutations vastly outweighs the number of possible graphs.
-For example, for the interacting two-hysteron system, there are eight switching fields, giving $8!
-= 40320$ permutations, and for $N=3$ the number of permutations is $24!
-\approx 6\times 10^{23}$.\\
-Instead of evaluating all permutations of the total order of the switching fields, we find it more useful to take a reverse approach by starting from the topology.
-We first construct a number of candidate graphs, which describe the behaviour of a hysteron system in a well-defined way but are not necessarily realizable.
-We then check whether each graph is realizable by evaluating whether there is a region in the parameter space of switching fields corresponding to the graph.\\
-The region in parameter space associated with each graph is bounded by a set of linear inequalities that the switching fields must obey, which we refer to as the design inequalities.
-We generate the design inequalities systematically by combining the conditions on each individual transition.
-We describe how the design inequalities are found in the Supplemental Information.
-If the solution space of a graph's design inequalities is not empty, then the graph is realizable.
-Thus, one can find the possible graphs for $N$ hysterons by first generating the candidate graphs, then checking whether each graph's design inequalities have a solution.\\
-In addition to being an efficient method for conclusively finding the possible graphs, the method of candidate graphs also allows us to consider rational design of graphs.
-We can use the candidate graph method to directly consider the possibility of the interesting behaviours that have been observed previously, such as multiperiodic cycles and long transients, for a  given number of hysterons.\
-We here establish our method for finding the transition graphs that are possible for coupled hysterons.
-We first discuss in section \ref{ssec:candidate_graphs} how one can generate a list of candidate graphs that includes all possible graphs for a given number of hysterons $N$.
-Next, in section \ref{ssec:realizability}, we explain how to evaluate whether or not a graph is realizable by checking whether its underlying design inequalities have a solution.
-Finally, we improve on the candidate graph method by introducing the concept of base graphs.
+Here we aim to establish a tool that can conclusively find all possible graphs for a given number of hysterons $N$.
+We base our method on the design inequalities, as introduced in Section \ref{ssec:ordering} and elaborated on in the Supplemental Information.
+We use the design inequalities to argue that the transitions that make up a graph, whether they are single flips or avalanches, can only be constructed out of a set collection of elementary steps.
+We use our method to construct a list of candidate graphs, then filter out the realizable graphs by explicitly checking the solution space of the design inequalities.\\
 \subsection{Candidate graphs}\label{ssec:candidate_graphs}

### 2022-06-29 Paper_draft.tex
Started work on base graph argument

@@
 \end{figure}
-We now describe two considerations that decrease the number of unique transition graphs, namely the 
+We now describe two considerations that decrease the number of unique transition graphs, namely exchange symmetry and the existence of Garden-of-Eden states. 
 \subsubsection{Exchange symmetry}
@@
 We base our method on the design inequalities, as introduced in Section \ref{ssec:ordering} and elaborated on in the Supplemental Information.
-We use the design inequalities to argue that the transitions that make up a graph, whether they are single flips or avalanches, can only be constructed out of a set collection of elementary steps.
+We use the design inequalities to argue that the transitions that make up a graph, whether they are single flips or avalanches, can only be constructed out of a fixed collection of elementary steps.
 We use our method to construct a list of candidate graphs, then filter out the realizable graphs by explicitly checking the solution space of the design inequalities.\\
@@
 \end{figure}
+\subsection{Base graphs}
+We now argue, based on the design inequalities, how avalanches must be constructed from a fixed choice of elementary steps.\\
+For the hysteron $i$ to flip up from the state $S$, the up switching field of hysteron $i$ must be the lowest of all the hysterons:
+\begin{equation}\label{eq:initial_transition}
+U_i^+(S) = \min_{s_j=0} U_j^+(S)
+\end{equation}
+Now suppose that the state $S$ is not stable, but is instead a part of an avalanche. Let $U*$ be the field at which the avalanche is initiated. Hysteron $i$ must then have
+\begin{equation}\label{eq:avalanche_unstable}
+U_i^+(S) \leq U*
+\end{equation}
+while all other hysterons $j$ with the state $s_j = 0$ must be stable, and therefore have
+\begin{equation}\label{eq:avalanche_stable}
+U_j^+(S) > U*
+\end{equation}
+Combining equations \ref{eq:avalanche_unstable} and \ref{eq:avalanche_stable}, we find that Equation \ref{eq:initial_transition} is implied.\\
 \subsection{Realizability}\label{ssec:realizability}

### 2022-07-01 Paper_draft.tex
Added reference to Mungan & Terzi (2020) for ordering of switching fields

@@
 When we fix the up switching fields to account for exchange symmetry, we find that the number of permutations is only $N!$.\\
-Indeed there are $N!$ Preisach graphs for a collection of $N$ hysterons, each corresponding to a different ordering of the down switching fields.
+Indeed there are $N!$ Preisach graphs for a collection of $N$ hysterons, each corresponding to a different ordering of the down switching fields\cite{terzimungan2020}.
 The ordering for each graph can be easily identified by considering the main loop: that is, the sequence of down transitions connecting the state with all $s_i = 1$ to that with all $s_i=0$.
 We accordingly use the main loop as an identifier for the Preisach graphs.
-For instance, for $N=2$ there are two Preisach graphs, corresponding to the main loops (1, 2) and (2, 1).\\
+For instance, for $N=2$ there are two Preisach graphs, corresponding to the main loops (1, 2) and (2, 1) \cite{terzimungan2020}.\\
 We have shown that it is straightforward to construct all Preisach graphs by considering all permutations of the down switching fields.

### 2022-07-01 Paper_draft.tex
Added comment that comparisons between up/down fields only occur with avalanches

@@
 \subsubsection{Exchange symmetry}
-The hysterons in our model are considered as indistinguishable particles.
-That is, when we define the state $S = \{s_1, s_2, ..., s_N\}$, the labelling of hysterons 1 through N is arbitrary.
+When we define the state $S = \{s_1, s_2, ..., s_N\}$, the labelling of hysterons 1 through N is arbitrary.
 As a result, when two graphs only differ from one another by the ordering of the hysterons 1, 2, ..., N, we consider the graphs to be the same (Fig.
@@
 To account for exchange symmetry, we fix the order in which hysterons 1, 2, ..., N flip up when increasing the external field from the ground state.
-For example, for $N=3$, we have that hysteron 3 flips up first from the state 000, hysteron 2 flips up first from 001, and trivially hysteron 1 flips up first from 011.
+For example, for $N=3$, we label the hysterons such that hysteron 3 flips up first from the state 000, hysteron 2 flips up first from 001, and trivially hysteron 1 flips up first from 011.
 Since there are $N!$ permutations of the order of $N$ up switching fields, accounting for exchange symmetry decreases the number of candidate graphs by a factor $N!$.
@@
 In the case where hysterons are non-interacting, there are only $2N$ switching fields $\{u_i^{+, -}\}$.
-In addition, because we never compare an up switching field with a down switching fields, the only orderings that can change the graph are the partial orderings of the up switching fields $\{u_i^+\}$ and of the down switching fields $\{u_i^-\}$.
+In addition, because we never compare an up switching field with a down switching fields in the absence of avalanches, the only orderings that can change the graph are the partial orderings of the up switching fields $\{u_i^+\}$ and of the down switching fields $\{u_i^-\}$.
 The number of orderings that can lead to a unique graph is then $N!\times N!$.

### 2022-07-01 Paper_draft.tex
Minor changes: 'the same' -> 'equivalent when comparing graphs, removed reference to hysterons as 'indistinguishable'
Changed 'we have shown that it is straightforward to construct all Preisach graphs' to 'there is a one-to-one relationship' as we do not show the process; changed linear model in intro ordering to general

@@
 When we define the state $S = \{s_1, s_2, ..., s_N\}$, the labelling of hysterons 1 through N is arbitrary.
-As a result, when two graphs only differ from one another by the ordering of the hysterons 1, 2, ..., N, we consider the graphs to be the same (Fig.
+As a result, when two graphs only differ from one another by the ordering of the hysterons 1, 2, ..., N, we consider the graphs to be equivalent (Fig.
 \ref{fig:exchangeplusgoe}a).\\
@@
 \subsection{Ordering of switching fields}\label{ssec:ordering}
-We now describe how the transition graph is constructed for a given set of bare switching fields $\{u_i^{+, -}\}$ and coupling coefficients $c_{ij}$.\\
+We now describe how the transition graph is constructed for a given set of switching fields $U_i^{+, -}(S)$.\\
+
 We observe that in essence, it is only the ordering of the switching fields ${U_i^{+, -}(S)}$ that determines the state transition graph, rather than their absolute value.
@@
 For instance, for $N=2$ there are two Preisach graphs, corresponding to the main loops (1, 2) and (2, 1) \cite{terzimungan2020}.\\
-We have shown that it is straightforward to construct all Preisach graphs by considering all permutations of the down switching fields.
+We see that for the Preisach model, there is a one-to-one relationship between the permutations in the orderings of the switching fields $u_i^{+, -}$ and the possible transition graphs.
 When hysterons are allowed to interact, however, the situation changes.
@@
 On the other hand, the state transition graph is only determined by a partial order between some of the switching fields.
-As a result, the number of permutations $(2(2^N-1))!$  for interacting hysterons greatly outnumbers the number of unique state transition graphs.
+As a result, the number of permutations of the switching fields $(2(2^N-1))!$  for interacting hysterons greatly outnumbers the number of unique state transition graphs.
 For $N=2$, the number of permutations is $8!

### 2022-07-05 Paper_draft.tex
Added explanation for building up a transition graph & image for initation/stability conditions

@@
 \subsection{Ordering of switching fields}\label{ssec:ordering}
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.5\textwidth]{initstability.pdf}
+    \caption{Linear inequalities imposed by initiation \& stability conditions of an example transition.}
+    \label{fig:initstability}
+\end{figure}
 We now describe how the transition graph is constructed for a given set of switching fields $U_i^{+, -}(S)$.\\
-
-We observe that in essence, it is only the ordering of the switching fields ${U_i^{+, -}(S)}$ that determines the state transition graph, rather than their absolute value.
-As a result, there can only be as many graphs as there are permutations of the order of switching fields.
+The possible transitions from a stable state $S$ of the system are found in two steps.
+First, we vary the external driving $U$ until it reaches a value where a hysteron flips, which we will call $U^*$.
+There are two possible transitions at each state, corresponding to an increase or decrease in the driving $U$.
+For an increase in the driving $U$, the first hysteron to flip is that with the lowest up switching field, which we denote as $U^+(S)$:
+\begin{equation}\label{eq:globalup}
+U^* = U^+(S) = \min_{s_j = 0}U_j^+(S)
+\end{equation}
+For a decrease in the driving $U$, the first hysteron to flip is that with the highest down switching field, which we call $U^-(S)$:
+\begin{equation}\label{eq:globaldown}
+U^* = U^-(S) = \max_{s_j = 1}U_j^+(S)
+\end{equation}\\
+After a hysteron is flipped, we let the system relax by holding the driving at $U^*$ until a new stable state is reached.
+Stability under the field $U^*$ means that all hysterons in phase $s_i=0$ have up switching fields higher than $U^*$, while all hysterons in phase $s_i = 1$ have down switching fields lower than $U^*$.
+By applying the two steps of initiation and stability to all stable states, we find the entire transition graph.
+\\
+We now consider how the values of the switching fields can influence the transition graph at each of the two steps.
+For the iniation, we only compare up switching fields with up switching fields, and down switching fields with down switching fields, at the same state $S$.
+At the second step, we compare both up switching fields and down switching fields with the current value of the driving, which is the field $U^*$ which initiates a transition.
+However, $U^*$ itself given by Equations \ref{eq:globalup} and \ref{eq:globaldown}, and thus equal to one of the switching fields $U_i^{+, -}(S)$.
+We remark that for both steps the transition graph only depends on a set of linear inequalities $U_i(S_A) > U_j(S_B)$.
+It follows that the transition graph is purely determined by the order of switching fields, rather than their absolute value.\\
 In the case where hysterons are non-interacting, there are only $2N$ switching fields $\{u_i^{+, -}\}$.

### 2022-07-06 Paper_draft.tex
Removed out-of-place reference to number of graphs in sections on exchange symmetry/GoE states; minor wording change in line 123

@@
 For example, for $N=3$, we label the hysterons such that hysteron 3 flips up first from the state 000, hysteron 2 flips up first from 001, and trivially hysteron 1 flips up first from 011.
-Since there are $N!$ permutations of the order of $N$ up switching fields, accounting for exchange symmetry decreases the number of candidate graphs by a factor $N!$.
-Thus, for $N=2$, the number of candidate graphs is reduced by a factor 2 from 2916 to 1458.
+Since there are $N!$ permutations of the order of $N$ up switching fields, accounting for exchange symmetry decreases the number of candidate graphs by a factor $N!$.\\
 \subsubsection{Garden-of-Eden states}
@@
 As a consequence of excluding GoE states, when two graphs only differ from one another by transitions that occur from GoE states, the graphs become duplicates.
-Therefore, when GoE states are ignored, the number of distinct graphs can turn out lower than the number of possible combinations of transitions.
-For $N=2$, ignoring GoE states  reduces the number of graphs from 1458 to 752.
+Therefore, when GoE states are ignored, the number of distinct graphs can turn out lower than the number of possible combinations of transitions.\\
 \subsection{Ordering of switching fields}\label{ssec:ordering}
@@
 The number of orderings that can lead to a unique graph is then $N!\times N!$.
-When we fix the up switching fields to account for exchange symmetry, we find that the number of permutations is only $N!$.\\
-Indeed there are $N!$ Preisach graphs for a collection of $N$ hysterons, each corresponding to a different ordering of the down switching fields\cite{terzimungan2020}.
-The ordering for each graph can be easily identified by considering the main loop: that is, the sequence of down transitions connecting the state with all $s_i = 1$ to that with all $s_i=0$.
+When we fix the up switching fields to account for exchange symmetry, we find that the number of permutations is only $N!$.
+Indeed there are $N!$ Preisach graphs for a collection of $N$ hysterons, each corresponding to a different ordering of the down switching fields\cite{terzimungan2020}.\\
+ The ordering for each Preisach graph can be easily identified by considering the main loop: that is, the sequence of down transitions connecting the state with all $s_i = 1$ to that with all $s_i=0$.
 We accordingly use the main loop as an identifier for the Preisach graphs.
@@
 For $N=3$, the number of permutations is as high as $24!
-\approx 6\times 10^{23}$.\\
-We thus see that it is inefficient to find all graphs for an interacting system of hysterons by considering the permutations of all switching fields.
+\approx 6\times 10^{23}$.
+The gross overestimation of the number of graphs makes it a challenge to find and identify all graphs for an interacting system of hysterons.\\
 Even so, we can make use of the fact that the state transition graph only depends on a partial ordering of the switching fields.

### 2022-07-08 Paper_draft.tex
Corrected lack of superscript for U^* in several instances
Typo correction: U_j^+ to U_j^- in line 119
Reworked argument on switching field ordering; introduction and conclusion are still unfinished

@@
 \end{figure}
-We now describe how the transition graph is constructed for a given set of switching fields $U_i^{+, -}(S)$.\\
-The possible transitions from a stable state $S$ of the system are found in two steps.
-First, we vary the external driving $U$ until it reaches a value where a hysteron flips, which we will call $U^*$.
+In this section we discuss the crucial role of the ordering of the switching fields $U_i^{+, -}(S)$ for the topology of the corresponding transition graph.
+(...) Moreover, we discuss how the ordering of the switching fields provides an easy way to generate and label the transition graphs for non-interacting hysterons, while for interacting hysterons this is more challenging.
+(...)\\
+To establish the importance of the ordering of the switching fields, we consider how a transition graph is constructed for a given set of switching fields.
+To start with, we ask which hysterons flip first from each state $S$, disregarding for the moment any avalanches that the initial hysteron flips might trigger\cite{grr}.
+To find the transitions from a state $S$, we vary the external driving $U$ until it reaches a value where a hysteron flips, which we will call $U^*$.
 There are two possible transitions at each state, corresponding to an increase or decrease in the driving $U$.
@@
 \end{equation}
-For a decrease in the driving $U$, the first hysteron to flip is that with the highest down switching field, which we call $U^-(S)$:
+while for a decrease in the driving $U$, the first hysteron to flip is that with the highest down switching field, which we call $U^-(S)$:
 \begin{equation}\label{eq:globaldown}
-U^* = U^-(S) = \max_{s_j = 1}U_j^+(S)
+U^* = U^-(S) = \max_{s_j = 1}U_j^-(S)
 \end{equation}\\
-After a hysteron is flipped, we let the system relax by holding the driving at $U^*$ until a new stable state is reached.
-Stability under the field $U^*$ means that all hysterons in phase $s_i=0$ have up switching fields higher than $U^*$, while all hysterons in phase $s_i = 1$ have down switching fields lower than $U^*$.
-By applying the two steps of initiation and stability to all stable states, we find the entire transition graph.
-\\
-We now consider how the values of the switching fields can influence the transition graph at each of the two steps.
-For the iniation, we only compare up switching fields with up switching fields, and down switching fields with down switching fields, at the same state $S$.
-At the second step, we compare both up switching fields and down switching fields with the current value of the driving, which is the field $U^*$ which initiates a transition.
-However, $U^*$ itself given by Equations \ref{eq:globalup} and \ref{eq:globaldown}, and thus equal to one of the switching fields $U_i^{+, -}(S)$.
-We remark that for both steps the transition graph only depends on a set of linear inequalities $U_i(S_A) > U_j(S_B)$.
-It follows that the transition graph is purely determined by the order of switching fields, rather than their absolute value.\\
+We observe that the Equations \ref{eq:globalup} and \ref{eq:globaldown} give conditions on the switching field which are linear inequalities, of the form $U_i^+(S) > U_j^+(S)$ and $U_i^-(S) > U_j^-(S)$.
+Notably, the linear inequalities of this form only impose an ordering between the switching fields $U_i^{+, -}(S)$.
+The values of the switching fields, as well as their relative distances, can be changed without changing the transition graph, so long as the ordering of the switching fields remains the same.
+Thus, to determine which hysterons can be flipped from each state, it is sufficient to know the ordering of the switching fields $\{U_i^{+, -}(S)\}$.\\
+We now show that the ordering between the switching fields is sufficient not just to determine the first hysteron flipped from each state, but to determine the entire transition graph, including any possible avalanches.
+To prove our statement, we look in detail at how a single transition is constructed.
+After the first hysteron has flipped, the system reaches a new state $S^{(1)}$.
+If the state $S^{(1)}$ is stable under $U^*$, then there is no avalanche.
+We call such a transition an elementary transition.
+If, however, the state $S^{(1)}$ is unstable, then an avalanche occurs and additional steps are required.\\
+We first look at the case of an elementary transition, where the state $S^{(1)}$ is stable under the current driving $U^*$.
+Stability of $S^{(1)}$ under $U^*$ means that all up switching fields $U_i^+(S^{(1)})$ are higher than the current driving $U^*$:
+\begin{equation}\label{eq:stableup}
+U_j^+(S^{(1)}) > U^* 
+\end{equation}
+while all down switching fields are lower than $U^*$:
+\begin{equation}\label{eq:stabledown}
+U_j^+(S^{(1)}) < U^* 
+\end{equation}
+Unlike Equations \ref{eq:globalup} and \ref{eq:globaldown}, the stability conditions in  Equations \ref{eq:stableup} and \ref{eq:stabledown} do not make a direct comparison between switching fields.
+Rather, the switching fields at state $S^{(1)}$ are compared to the current driving, which is $U^*$.
+However, $U^*$ itself is given by Equations \ref{eq:globalup} and \ref{eq:globaldown}, and therefore equal to one of the switching fields $U_i^{+, -}(S)$.
+Thus the stability of $S^{(1)}$ depends, once again, purely on the ordering of the switching fields.\\
+Next we consider the additional steps that are required when $S^{(1)}$ is unstable.
+The system then enters into a new state $S^{(2)}$, for which we once again need to check the stability under the current driving.
+The current driving is still held at $U^*$, so the stability conditions are as in Equations \ref{eq:stableup} and \ref{eq:stabledown}, except that the state $S^{(1)}$ is now replaced by $S^{(2)}$.
+Thus, if the state $S^{(2)}$ is stable, we obtain a set of linear inequalities as in Equations \ref{eq:stableup} and \ref{eq:stabledown}.
+If the state $S^{(2)}$ is unstable, then the system moves to a third state $S^{(3)}$, and in this way the system can keep iterating through states until a stable state is reached.
+For each new state a corresponding set of inequalities is added, and each set of inequalities thus obtained only depends on the ordering of the switching fields.
+Hence, any transition $S \rightarrow S^{(1)} \rightarrow ...
+\rightarrow S^{(l)}$, of any length $l$, is fully determined from the ordering of the switching fields.\\
+Finally, we state that the full transition graph is described by a set of inequalities that is simply a combination of the conditions on the individual transitions.(...)We conclude that the corresponding transition graph for a set of switching fields only depends on the ordering of the switching fields, as described by a set of linear inequalities.
+We refer to the set of inequalities underlying a graph as the design inequalities\cite{vhecke2021}.\\
+
 In the case where hysterons are non-interacting, there are only $2N$ switching fields $\{u_i^{+, -}\}$.
@@
 \end{equation}
-Now suppose that the state $S$ is not stable, but is instead a part of an avalanche. Let $U*$ be the field at which the avalanche is initiated. Hysteron $i$ must then have
+Now suppose that the state $S$ is not stable, but is instead a part of an avalanche. Let $U^*$ be the field at which the avalanche is initiated. Hysteron $i$ must then have
 \begin{equation}\label{eq:avalanche_unstable}
-U_i^+(S) \leq U*
+U_i^+(S) \leq U^*
 \end{equation}
@@
 \begin{equation}\label{eq:avalanche_stable}
-U_j^+(S) > U*
+U_j^+(S) > U^*
 \end{equation}

### 2022-07-14 Paper_draft.tex
Added comments to text; minor changes

@@
 \usepackage[table]{xcolor}
+\usepackage{multirow}
+\usepackage{slashbox}
 \newcommand\note[1]{\textcolor{red}{#1}}
+\newcommand\workon[1]{\textcolor{blue}{#1}}
+\newcommand\fillin[1]{\textcolor{teal}{\textbf{#1}}}
 \usepackage{amsmath}
@@
 Here we establish a systematic method to gradually approach the complexity of the interacting hysteron model, starting from the Preisach model.
-We first establish a formalism for constructing the transition graph for coupled hysterons by starting from a Preisach graph, and adding the effects of coupling step-by-step.
+\workon{We first establish a formalism for constructing the transition graph for coupled hysterons by starting from a Preisach graph, and adding the effects of coupling step-by-step.
 We show how this formalism is used to construct a list of candidate graphs for a given number of hysterons.
 We then detail a method for checking whether a given transition graph can be realized, both in general and for a specific model.
-Finally, we illustrate our formalism for a model where hysterons are linearly coupled.\\
+Finally, we illustrate our formalism for a model where hysterons are linearly coupled.}\note{REWORK ACCORDING TO CURRENT STRUCTURE}\\
 \section{Model}\label{sec:model}
@@
 \end{equation}
- When a driving field $U$ is applied to a system with the collective state $S$, any hysterons that are in phase 0 and have $U \geq U_i^+$, or that are in phase 1 and have $U \leq U_i^-$, become unstable.
+ \workon{When a driving field $U$ is applied to a system with the collective state $S$, any hysterons that are in phase 0 and have $U \geq U_i^+$, or that are in phase 1 and have $U \leq U_i^-$, become unstable.
 If a single hysteron is unstable, that hysteron flips.
@@
 It is also possible that an avalanche leads back into the state itself, in which case the system becomes caught in a self-loop.
-We consider this scenario to be ill-defined, as the system's state is caught in an infinite loop.\\
-The system's response to a field $U$ is thus obtained by comparing the field to the switching fields $\{U_i^+\}, \{U_i^-\}$ of the hysterons individually, flipping hysterons that are unstable, and repeating this process until there are no more unstable hysterons.
-The response is ill-defined if multiple hysterons are unstable at the same time, or if the system becomes caught in an infinite self-loop.\\
+We consider this scenario to be ill-defined, as the system's state is caught in an infinite loop.}\note{TALK ABOUT ILL-DEFINED LAST}\\
+\workon{The system's response to a field $U$ is thus obtained by comparing the field to the switching fields $\{U_i^+\}, \{U_i^-\}$ of the hysterons individually, flipping hysterons that are unstable, and repeating this process until there are no more unstable hysterons.
+The response is ill-defined if multiple hysterons are unstable at the same time, or if the system becomes caught in an infinite self-loop.}\note{REPETITIVE}\\
 The possible responses of a collection of $N$ hysterons to driving are captured by a state transition graph, which consists of all stable states $S$ and all transitions between states.
@@
 It can occur that not all of the $2^N$ states are included in the transition graph, because it is possible for a state to not be reachable, or to only be reachable as an unstable intermediate state of an avalanche.
-We now make two considerations that affect the number of distinct graphs, namely exchange symmetry and Garden-of-Eden states.
+\fillin{(...)} We now make two considerations that affect the number of distinct graphs, namely exchange symmetry and Garden-of-Eden states.
 \subsection{Uniqueness considerations}
@@
 \subsubsection{Garden-of-Eden states}
-It often occurs that one or more of the possible states for $N$ hysterons cannot be reached from the ground state.
+It often occurs that one or more of the possible states for $N$ hysterons cannot be reached from the \workon{ground state}\note{NOT DEFINED}.
 As is customary\cite{juleslechenault2021}, we refer to states that cannot be reached as garden-of-Eden (GoE) states.
@@
     \includegraphics[width=0.5\textwidth]{initstability.pdf}
-    \caption{Linear inequalities imposed by initiation \& stability conditions of an example transition.}
+    \caption{Linear inequalities imposed by initiation \& stability conditions of an example transition. \note{NO REFERENCE TO THIS FIG}}
     \label{fig:initstability}
@@
 In this section we discuss the crucial role of the ordering of the switching fields $U_i^{+, -}(S)$ for the topology of the corresponding transition graph.
-(...) Moreover, we discuss how the ordering of the switching fields provides an easy way to generate and label the transition graphs for non-interacting hysterons, while for interacting hysterons this is more challenging.
-(...)\\
+\fillin{(...)}\note{BRIEF OVERVIEW} Moreover, we discuss how the ordering of the switching fields provides an easy way to generate and label the transition graphs for non-interacting hysterons, while for interacting hysterons this is more challenging.
+\fillin{(...)}\note{CONCLUSION}\\
 To establish the importance of the ordering of the switching fields, we consider how a transition graph is constructed for a given set of switching fields.
-To start with, we ask which hysterons flip first from each state $S$, disregarding for the moment any avalanches that the initial hysteron flips might trigger\cite{grr}.
+\workon{To start with, we ask which hysterons flip first from each state $S$, disregarding for the moment any avalanches that the initial hysteron flips might trigger\cite{grr}}\note{WHERE TO MENTION AVALANCHES?}.
 To find the transitions from a state $S$, we vary the external driving $U$ until it reaches a value where a hysteron flips, which we will call $U^*$.
-There are two possible transitions at each state, corresponding to an increase or decrease in the driving $U$.
+There are two possible transitions at each state, corresponding to an increase or decrease in the driving $U$\cite{grr}.
 For an increase in the driving $U$, the first hysteron to flip is that with the lowest up switching field, which we denote as $U^+(S)$:
@@
 The system then enters into a new state $S^{(2)}$, for which we once again need to check the stability under the current driving.
-The current driving is still held at $U^*$, so the stability conditions are as in Equations \ref{eq:stableup} and \ref{eq:stabledown}, except that the state $S^{(1)}$ is now replaced by $S^{(2)}$.
+\note{ALSO OLD STABILITY CONDITIONS W/ ONE INEQ FLIPPED}\workon{The current driving is still held at $U^*$, so the stability conditions are as in Equations \ref{eq:stableup} and \ref{eq:stabledown}, except that the state $S^{(1)}$ is now replaced by $S^{(2)}$.
 Thus, if the state $S^{(2)}$ is stable, we obtain a set of linear inequalities as in Equations \ref{eq:stableup} and \ref{eq:stabledown}.
-If the state $S^{(2)}$ is unstable, then the system moves to a third state $S^{(3)}$, and in this way the system can keep iterating through states until a stable state is reached.
-For each new state a corresponding set of inequalities is added, and each set of inequalities thus obtained only depends on the ordering of the switching fields.
+If the state $S^{(2)}$ is unstable, then the system moves to a third state $S^{(3)}$, and in this way the system can keep iterating through states until a stable state is reached.} \note{TOO QUICK} For each new state a corresponding set of inequalities is added, and each set of inequalities thus obtained only depends on the ordering of the switching fields.
 Hence, any transition $S \rightarrow S^{(1)} \rightarrow ...
-\rightarrow S^{(l)}$, of any length $l$, is fully determined from the ordering of the switching fields.\\
-Finally, we state that the full transition graph is described by a set of inequalities that is simply a combination of the conditions on the individual transitions.(...)We conclude that the corresponding transition graph for a set of switching fields only depends on the ordering of the switching fields, as described by a set of linear inequalities.
+\rightarrow S^{(l)}$, of any length $l$, is fully determined from the ordering of the switching fields.\note{INITIAL STATE $S$ OR $S^{(0)}$?}\\
+Finally, we state that the full transition graph is described by a set of inequalities that is simply a combination of the conditions on the individual transitions.\fillin{(...)}We conclude that the corresponding transition graph for a set of switching fields only depends on the ordering of the switching fields, as described by a set of linear inequalities.
 We refer to the set of inequalities underlying a graph as the design inequalities\cite{vhecke2021}.\\
-
+\workon{
 In the case where hysterons are non-interacting, there are only $2N$ switching fields $\{u_i^{+, -}\}$.
@@
 We accordingly use the main loop as an identifier for the Preisach graphs.
-For instance, for $N=2$ there are two Preisach graphs, corresponding to the main loops (1, 2) and (2, 1) \cite{terzimungan2020}.\\
+For instance, for $N=2$ there are two Preisach graphs, corresponding to the main loops (1, 2) and (2, 1) \cite{terzimungan2020}.
+\\
 We see that for the Preisach model, there is a one-to-one relationship between the permutations in the orderings of the switching fields $u_i^{+, -}$ and the possible transition graphs.
@@
 The solution space of the design inequalities provides the region in parameter space that leads to the given graph.
-In particular, if the design inequalities have no solution, then the given graph is not realizable.\\
+In particular, if the design inequalities have no solution, then the given graph is not realizable.} \note{REWORK; SEE OUTLINE}\\
 \section{Constructing possible graphs}
-In recent work, the transition graphs for two- and three-hysteron systems were found using numerical sampling.
+\workon{In recent work, the transition graphs for two- and three-hysteron systems were found using numerical sampling.
 The obtained graphs contain several noteworthy phenomena that are not possible in the Preisach model, such as breaking of loop return point memory, scrambling, multiperiodic cycles and long transients\cite{vhecke2021}.\\
-A significant disadvantage of numerical sampling is that it is not conclusive, as it is always possible that a region in parameter space leading to a certain transition graph is missed.
-Here we aim to establish a tool that can conclusively find all possible graphs for a given number of hysterons $N$.
+A significant disadvantage of numerical sampling is that it is not conclusive, as it is always possible that a region in parameter space leading to a certain transition graph is missed.}\note{MOVE EARLIER} Here we aim to establish a tool that can conclusively find all possible graphs for a given number of hysterons $N$.
 We base our method on the design inequalities, as introduced in Section \ref{ssec:ordering} and elaborated on in the Supplemental Information.
@@
 \subsection{Candidate graphs}\label{ssec:candidate_graphs}
-A well-defined transition graph for $N$ hysterons consists out of $2^N$ states, and $2(2^N-1)$ transitions, namely the up and down transitions from each state, except for the saturated states which only have one transition each.
+\workon{A well-defined transition graph for $N$ hysterons consists out of $2^N$ states, and $2(2^N-1)$ transitions, namely the up and down transitions from each state, except for the saturated states which only have one transition each.
 A transition graph is constructed by choosing a transition path for each of these $2(2^N-1)$ transitions.
 A transition path may be a single hysteron flip, or may consist of multiple flipped hysterons.
-When a transition path consists of multiple hysteron flips, we speak of an avalanche.\\
-Naively, one can construct all possible transition graphs by finding the possible transition paths for each individual transition.
-For example, for $N=2$ one finds $3^4\times 6^2 = 2916$ graphs (Fig.\ref{fig:transition_paths_N2}).\\
+When a transition path consists of multiple hysteron flips, we speak of an avalanche.}\note{COMBINE W/ PREVIOUS SECTION}\\
+\workon{Naively, one can construct all possible transition graphs by finding the possible transition paths for each individual transition.
+For example, for $N=2$ one finds $3^4\times 6^2 = 2916$ graphs (Fig.\ref{fig:transition_paths_N2})}\note{START W/ BASE GRAPHS}.\\
 \begin{figure}[ht!]
@@
 Combining equations \ref{eq:avalanche_unstable} and \ref{eq:avalanche_stable}, we find that Equation \ref{eq:initial_transition} is implied.\\
+\fillin{(...)}\\
 \subsection{Realizability}\label{ssec:realizability}
-To better understand why some graphs are not realizable,  we look in detail at the design inequalities underlying the graphs (see SI), and identify the inequalities that are in conflict with one another.
+\workon{To better understand why some graphs are not realizable,  we look in detail at the design inequalities underlying the graphs (see SI), and identify the inequalities that are in conflict with one another.
 By then tracing these inequalities back to the transitions from which we arise, we find the combinations of transitions (i.e., subgraphs) that are incompatible and thus make a graph not realizable.
 Several examples of impossible subgraphs are given in Fig.
-\ref{fig:impossiblegraphs}a.\\
-We now direct our attention to a particular group of impossible subgraphs, an example of which is shown in Fig.
+\ref{fig:impossiblegraphs}a.}\note{WHERE TO TALK ABOUT INCOMPATIBLE SUBGRAPHS?}\\
+\workon{We now direct our attention to a particular group of impossible subgraphs, an example of which is shown in Fig.
 \ref{fig:impossiblegraphs}b.
@@
 The argument used for the example subgraph can be extended to the general argument that the up and down flips which can occur from a state do not depend on whether or not that state is stable.
-As a consequence, all avalanches occuring in a graph must conform to an underlying graph of single-flip transitions, which we refer to as the base graph.
-\\
+As a consequence, all avalanches occuring in a graph must conform to an underlying graph of single-flip transitions, which we refer to as the base graph.}\note{PART OF BASE GRAPH ARGUMENT} \\
 Using base graphs, we can improve upon our method for generating candidate graphs.
@@
 \node[squarednode](mainloop){Main loop};
-\node[squarednode](scrambling)[right=of mainloop] {Scrambling};
-\node[squarednode](avalanches)[right=of scrambling] {Avalanches};
-\node[squarednode](finalgraph)[right=of avalanches] {Final graph};
+\node[squarednode](scrambling) [right = 0.5 of mainloop]{Scrambling};
+\node[squarednode](avalanches)[right=0.5 of scrambling] {Avalanches};
+\node[squarednode](finalgraph)[right=0.5 of avalanches] {Final graph};
 
@@
 \end{tikzpicture}
-    \caption{Breakdown of an example transition graph into a base graph and a combination of avalanches.
-The base graph can itself be separated into the main loop and a number of scrambled transitions.}
+    \caption{Schematic of the construction of a graph via the base graph method.
+The base graph can itself be separated into the main loop and a number of scrambled transitions.\note{NO REFERENCE TO THIS FIG}}
     \label{fig:basegraphs_avalanches}
@@
 \subsubsection{Base graphs}
+\begin{table}[h!]
+\begin{tabular}{l|l|ll|ll|}
+\cline{2-6}
+                                        &  & \multicolumn{2}{l|}{}    & \multicolumn{2}{l|}{}    \\ \hline
+\multicolumn{1}{|l|}{}                  &  & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} &  \\ \hline
+\multicolumn{1}{|l|}{\multirow{2}{*}{}} &  & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} &  \\ \cline{2-6} 
+\multicolumn{1}{|l|}{}                  &  & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} &  \\ \hline
+\multicolumn{1}{|l|}{\multirow{2}{*}{}} &  & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} &  \\ \cline{2-6} 
+\multicolumn{1}{|l|}{}                  &  & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} &  \\ \hline
+\end{tabular}
+\end{table}
 We here show how we generate the list of base graphs for $N$ hysterons, which is subsequently used to construct the full list of candidate graphs.
@@
 First, there are the Preisach graphs, which are possible without coupling.
-Second, there is a group of scrambled graphs, which are possible for interacting hysterons.
+\workon{Second, there is a group of scrambled graphs, which are possible for interacting hysterons.
 Scrambling is a phenomenon previously seen in interacting hysterons\cite{vhecke2021}\cite{bense2021}, where the order in which hysterons flip is not the same throughout the graph.
@@
 Remarkably, having introduced the concept of base graphs, we can identify scrambling as a feature of the base graph.
-We can thus separate the two coupling effects of scrambling and avalanches.\\
-In order to discuss scrambling more explicitly, we here define the main loop as the series of up and down transitions connecting the two saturated states.
+We can thus separate the two coupling effects of scrambling and avalanches.}\note{TOO QUICK; BUILD UP TO SCRAMBLING GRADUALLY}\\
+\workon{In order to discuss scrambling more explicitly, we here define the main loop as the series of up and down transitions connecting the two saturated states.
 In the Preisach model, the ordering of the main loop fixes the transitions throughout the transition graph, so that each main loop corresponds to a unique Preisach graph.
@@
 However, we fix the up boundary when accounting for exchange symmetry, thus dividing the number of main loops by $N!$.
-Therefore, when accounting for exchange symmetry, there are only $N!$ main loops and resulting Preisach graphs.\\
+Therefore, when accounting for exchange symmetry, there are only $N!$ main loops and resulting Preisach graphs.}\note{REFER BACK TO ORDERING SECTION}\\
 In a scrambled graph, one or more of the transitions in the graph deviates from the main loop, so that each main loop corresponds to a number of base graphs (Table.\ref{fig:basegraphs_n3}).\\
@@
 From the possible $l=3$ avalanches, we can again construct a list of candidate graphs.\\
-We now ask which $L=2$ graphs should be used as our new 'base' for the $L=3$ graphs.
+We now ask which $L=2$ graphs should be used as our new \workon{'base'}\note{AVOID CONFUSION W/ BASE GRAPHS} for the $L=3$ graphs.
 It is insufficient to use only the $L=2$ graphs that are themselves realizable, as it is not guaranteed that a derived $L=3$ graph will also be impossible.\\

### 2022-07-14 Paper_draft.tex
Added figure to show base graphs for single main loop & GoE pruning

@@
 \subsubsection{Base graphs}
-\begin{table}[h!]
-\begin{tabular}{l|l|ll|ll|}
+\begin{table*}[]
+\begin{tabular}{c|c|cc|cc|}
 \cline{2-6}
-                                        &  & \multicolumn{2}{l|}{}    & \multicolumn{2}{l|}{}    \\ \hline
-\multicolumn{1}{|l|}{}                  &  & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} &  \\ \hline
-\multicolumn{1}{|l|}{\multirow{2}{*}{}} &  & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} &  \\ \cline{2-6} 
-\multicolumn{1}{|l|}{}                  &  & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} &  \\ \hline
-\multicolumn{1}{|l|}{\multirow{2}{*}{}} &  & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} &  \\ \cline{2-6} 
-\multicolumn{1}{|l|}{}                  &  & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} &  \\ \hline
+                                        & 100, up & \multicolumn{2}{c|}{3}    & \multicolumn{2}{c|}{2}    \\ \hline
+\multicolumn{1}{|c|}{110, down}                  & \backslashbox{101,  down}{010,  up} & \multicolumn{1}{c|}{3} &  1& \multicolumn{1}{c|}{3} &  1\\ \hline
+\multicolumn{1}{|c|}{\multirow{2}{*}{1}} &  1& \multicolumn{1}{c|}{ \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph10.pdf}} &  \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph2.pdf} & \multicolumn{1}{c|}{ \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph8.pdf}} &    \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph0.pdf}\\ \cline{2-6}
+\multicolumn{1}{|c|}{}                  &  3& \multicolumn{1}{c|}{ \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph14.pdf}} &   \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph6.pdf}& \multicolumn{1}{c|}{ \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph12.pdf}} &  \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph4.pdf}\\ \hline
+\multicolumn{1}{|c|}{\multirow{2}{*}{2}} &  1& \multicolumn{1}{c|}{ \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph11.pdf}} &  \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph3.pdf} & \multicolumn{1}{c|}{ \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph9.pdf}} &   \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph1.pdf}\\ \cline{2-6}
+\multicolumn{1}{|c|}{}                  &  3& \multicolumn{1}{c|}{ \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph15.pdf}} &  \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph7.pdf} & \multicolumn{1}{c|}{ \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph13.pdf}} &   \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph5.pdf}\\ \hline
 \end{tabular}
-\end{table}
+\caption{All sixteen base graphs for the example main loop (1, 3, 2).
+GoE pruning reduces the number of distinct base graphs from sixteen to four, out of which three are solvable in the linear model.
+\note{NO REFERENCE TO THIS FIG}}
+\label{fig:goepruning}
+\end{table*}
 We here show how we generate the list of base graphs for $N$ hysterons, which is subsequently used to construct the full list of candidate graphs.
